---
title: | 
 | PASS1A (Rat) Metabolomics: 
 | Site-Specific EDA--Mayo Clinic
author: "Alec Steep"
date: "10/12/2020"
output:
     html_document:
         code_folding: hide
         toc: true
         highlight: zenburn
         css: ../css/style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(cache = FALSE)
```

##### CSS Top Styling
```{r CSS Top Styling}
writeLines("td, th { padding : 3px } th { background-color:white; color:black; border:1px solid black; text-align:center } td {color:black; border:1px solid black; word-wrap:break-word; white-space:nowrap; overflow: hidden; text-overflow: ellipsis; max-width:300px; text-align:left}", con= "../css/style.css")

```

## Goals of Analysis
  + Identify biological replicates from Mayo across tissues
  + Compare replicate sample pairs
    + Identify metabolites with missing values
    + Plot and measure correlation of metabolite abundances before and after correlation
    + Perform PCA analysis between sets of replicate pairs

#### Mayo-specific Annotations
  + All targeted
  + No normalization
  + No drift correction
  + No imputation
  + Samples were divided into batches of ~20 [samples] for analysis

#### Questions for Mayo:
  + What was the role of QC_POOLED and QC_REFERENCE samples?
  + How were QC samples divided across runs?
  + "raw_file" seems to represent a date and an additiona number (date_#)
    + What is the significance of this number? Does it represent a sample order
  + How was "sample_order" determined?
  + How were batches divided across samples and QCs?
  + Why were some tissues replicated?
  + Demonstrate correlation (or lack thereof) for certain replicate runs.

#### Metabolite Families and tissues with replicate pairs
  + Metabolite families:
    + ac, amines, cer, tca
  + Within Tissues:
    + liver, gastrocnemius, white-adipose, lung, heart, brown-adipose, kidney

### Setup the Top Environment
```{r Setup the Top Environment, message=FALSE, results='hide', warning = FALSE}
################################################################################
##### Resources and Dependencies ###############################################
################################################################################

# To Render the Markdown, run this line in console
#rmarkdown::render('/Volumes/Frishman_4TB/motrpac/20200915_metabolomics-pass1a/scripts/20201012_pass1a-metabolomics-data-cleanup_steep.Rmd', output_file = '/Volumes/Frishman_4TB/motrpac/20200915_metabolomics-pass1a/reports/mayo_clinic/20201012_replicate-analysis-AAll-tissues-Mayo-Clinic_steep.html')

# Set the working directory
#############################################################################
COMP <- "MacBook" 
#COMP <- "GreatLakes"       
if(COMP == "MacBook"){
        # MacBook
        WD <- '/Volumes/Frishman_4TB/motrpac/20200915_metabolomics-pass1a'    
}else if(COMP == "GreatLakes"){
        # MichMed
        WD <- '/home/acsteep/motrpac/20200915_metabolomics-pass1a'
}

#setwd(WD)

# Load the dependencies
#source("https://bioconductor.org/biocLite.R")
#BiocManager::install("org.Rn.eg.db")
#install.packages("kableExtra")

# Load dependencies
pacs...man <- c("tidyverse", "data.table","rlang","RColorBrewer","MASS","sfsmisc",
                "pheatmap","caret","ggforce","RANN","kableExtra","gtools","combinat",
                "knitr","markdown","rmarkdown")
for(pac in pacs...man){
  suppressWarnings(suppressPackageStartupMessages(library(pac, character.only = TRUE)))
}
# lapply(pacs...man, FUN = function(X) {
#         do.call("library", list(X)) })

############################################################
##### Functions ############################################
############################################################

# Name functions
select <- dplyr::select
counts <- DESeq2::counts
map <- purrr::map
desc <- dplyr::desc
arrange <- dplyr::arrange
melt <- reshape2::melt
mutate <- dplyr::mutate

# Global options
options(dplyr.print_max = 100)
options(scipen=10000)

# Source the functions
source(paste0(WD,'/functions/not_in.R'))
source(paste0(WD,'/functions/rat_mouse_ortho.R'))
source(paste0(WD,'/functions/mouse2rat_ortho.R'))
source(paste0(WD,'/functions/lmp.R'))
source(paste0(WD,'/functions/cor_PC_1_6.R'))
source(paste0(WD,'/functions/elbow_finder.R'))
source(paste0(WD,'/functions/cor_outlier2.R'))
source(paste0(WD,'/functions/DissimilarityMatrixNominal.R'))
source(paste0(WD,'/functions/lm_eqn.R'))
source(paste0(WD,'/functions/reorder_cormat.R'))
source(paste0(WD,'/functions/save_pheatmap_pdf.R'))
source(paste0(WD,'/functions/modeav.R'))
source(paste0(WD,'/functions/count_na.R'))
source(paste0(WD,'/functions/se_mean.R'))
source(paste0(WD,'/functions/Mode.R'))
source(paste0(WD,'/functions/NumericSummaryStats.R'))
source(paste0(WD,'/functions/AutoScaleMatrix.R'))
source(paste0(WD,'/functions/ReverseAutoScaleMatrix.R'))
source(paste0(WD,'/functions/CenterMatrix.R'))
source(paste0(WD,'/functions/RangeScaleMatrix.R'))
source(paste0(WD,'/functions/ParetoScaleMatrix.R'))
source(paste0(WD,'/functions/VastScaleMatrix.R'))
source(paste0(WD,'/functions/LevelScaleMatrix.R'))
source(paste0(WD,'/functions/Log10Matrix.R'))
source(paste0(WD,'/functions/PowerMatrix.R'))

```

### Load the Data
```{r Load Count Data & MetaData}
# Load the Data
################################################################################
# Files
metadata_rds <- paste0(WD, '/data/20201010_pass1a-metabolomics-metadata-table_steep.rds')
# Load Data
metadata_df <- readRDS(file = metadata_rds)

# Start the clock
ptm <- proc.time()
# Takes 21+ seconds (881.6 Mb) 1073+ seconds for (7.5Gb)
#countdata_rds <- paste0(WD, #'/data/20201010_pass1a-metabolomics-countdata-nested_steep.rds')

# Load a specific tissues count data
# Liver takes 230 seconds (4 min)
#countdata_rds <- paste0(WD, '/data/20201010_pass1a-metabolomics-countdata-nested-',tissue,'_steep.rds')

# Load a specific metabolite family count data
# ac takes 2 seconds
# hilicpos takes 453 seconds (on MB) or 260 seconds (on GL with 40 MB 2 cores)
# All data (original + autoscaled) takes 170 seconds on MB
countdata_rds <- paste0(WD, '/data/20201010_pass1a-metabolomics-countdata-nested_steep.rds')

# Load the data
countdata_df <- readRDS(file = countdata_rds)

# Stop the clock
#proc.time() - ptm
```

### Metadata
```{r Metadata Format}
metadata_df %>%
  head %>% 
  knitr::kable(format = "html") %>%
  scroll_box(width = "100%", height = "200px")
```

### Count Data
```{r Count Data Format}
countdata_df %>%
  head %>%
  knitr::kable(format = "html") %>%
  scroll_box(width = "100%", height = "200px")
```

### Load, Incorporate, & Display the Phenotype Data
```{r Incorporate Phenotype Data, results='asis'}
# Load the phenotype data
pheno_obj <- paste0(WD,"/data/20201021_pass1a-06-pheno-viallabel_steep.rds")
pheno_df <- readRDS(pheno_obj)

# Set a vector for Exercise/Control Levels and Colors
ec_levels <- c('Exercise - IPE',
               'Exercise - 0.5 hr',
               'Exercise - 1 hr',
               'Exercise - 4 hr',
               'Exercise - 7 hr',
               'Exercise - 24 hr',
               'Exercise - 48 hr',
               'Control - IPE',
               'Control - 7 hr')
ec_colors <- c('gold',
               'darkgoldenrod1',
               'orange',
               'darkorange',
               'darkorange2',
               'darkorange3',
               'darkorange4',
               'steelblue1',
               'steelblue4')

pheno_df %>%
  head(n = 20) %>% 
  knitr::kable(format = "html") %>%
  scroll_box(width = "100%", height = "200px")
```

### Visualize the number of samples and number of metabolites across all "named" batches
```{r Explore Metadata}

# Order of Sites and metab_family
site_metab_order <- metadata_df %>%
  unite(STUDY_INSTITUTE, METAB_FAMILY, col = "SITE_METAB") %>%
  select(TISSUE,SITE_METAB,SAMPLE_N,QC_IS_N,QC_PRERUN_N,QC_BLANK_N,
          QC_POOLED_N,QC_REFERENCE_N,QC_DRIFT_N,METABOLITE_N) %>%
  group_by(SITE_METAB) %>%
  select(SITE_METAB,SAMPLE_N) %>%
  mutate(SAMPLE_SUM = sum(SAMPLE_N)) %>%
  select(SITE_METAB, SAMPLE_SUM) %>%
  arrange(desc(SAMPLE_SUM)) %>% unique() %>%
  select(SITE_METAB) %>% unlist() %>% as.character() %>% unique()

# Order of tissues
tissue_order <- metadata_df %>%
  unite(STUDY_INSTITUTE, METAB_FAMILY, col = "SITE_METAB") %>%
  select(TISSUE,SITE_METAB,SAMPLE_N,QC_IS_N,QC_PRERUN_N,QC_BLANK_N,
          QC_POOLED_N,QC_REFERENCE_N,QC_DRIFT_N,METABOLITE_N) %>%
  group_by(TISSUE) %>%
  mutate(SAMPLE_SUM = sum(SAMPLE_N)) %>%
  select(TISSUE, SAMPLE_SUM) %>%
  arrange(desc(SAMPLE_SUM)) %>% unique() %>%
  select(TISSUE) %>% unlist() %>% as.character() %>% unique() %>% rev()
  
# Create a plot of sample number by tissue and technology
metadata_df %>%
  unite(STUDY_INSTITUTE, METAB_FAMILY, col = "SITE_METAB") %>%
  select(TISSUE,SITE_METAB,SAMPLE_N,QC_IS_N,QC_PRERUN_N,QC_BLANK_N,
          QC_POOLED_N,QC_REFERENCE_N,QC_DRIFT_N,METABOLITE_N) %>%
  mutate(TISSUE = factor(TISSUE, levels = tissue_order)) %>%
  mutate(SITE_METAB = factor(SITE_METAB, levels = site_metab_order)) %>%
  ggplot(aes(SITE_METAB,TISSUE)) +
    geom_tile(aes(fill = SAMPLE_N)) + 
    geom_text(aes(label = SAMPLE_N)) +
    scale_fill_gradient(low = "white", high = "red") +
  ggtitle("Samples Across Named Runs") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.title.x = element_blank(),
  axis.title.y = element_blank()) +
  theme(legend.position = "none") +
  scale_x_discrete(position = "top") +
  theme(axis.text.x = element_text(angle = 300, hjust = 0.9))

# METABOLITE_NAMED_N
# Create a plot of sample number by tissue and technology
metadata_df %>%
  unite(STUDY_INSTITUTE, METAB_FAMILY, col = "SITE_METAB") %>%
  select(TISSUE,NAMED,SITE_METAB,SAMPLE_N,QC_IS_N,QC_PRERUN_N,QC_BLANK_N,
          QC_POOLED_N,QC_REFERENCE_N,QC_DRIFT_N,METABOLITE_N) %>%
  mutate(TISSUE = factor(TISSUE, levels = tissue_order)) %>%
  mutate(SITE_METAB = factor(SITE_METAB, levels = site_metab_order)) %>%
  filter(NAMED == 'named') %>%
  mutate(METABOLITE_NAMED_N = 0) %>%
  mutate(METABOLITE_NAMED_N = ifelse(NAMED == 'named', METABOLITE_N, METABOLITE_NAMED_N)) %>%
  ggplot(aes(SITE_METAB,TISSUE)) +
    geom_tile(aes(fill = METABOLITE_NAMED_N)) + 
    geom_text(aes(label = METABOLITE_NAMED_N)) +
    scale_fill_gradient(low = "white", high = "red") +
  ggtitle("Named Metabolites Across Runs") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.title.x = element_blank(),
  axis.title.y = element_blank()) +
  theme(legend.position = "none") +
  scale_x_discrete(position = "top") +
  theme(axis.text.x = element_text(angle = 300, hjust = 0.9))

```

### Explore How Samples were Divided into Batches:
  + "Samples were divided into batches of ~20 [samples] for analysis"

```{r Batches of 20}
# Assign Variables
################################################################################
tissue_study_institute_metab_families <- countdata_df %>%
  ungroup() %>%
  filter(STUDY_INSTITUTE == 'Mayo Clinic') %>%
  unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
  unite(TISSUE,STUDY_INSTITUTE_METAB_FAMILY, col = TISSUE_STUDY_INSTITUTE_METAB_FAMILY) %>%
  select(TISSUE_STUDY_INSTITUTE_METAB_FAMILY) %>% unlist() %>% as.character() %>% unique()

# Are all samples divisible by 20?
metadata_df %>%
  unite(STUDY_INSTITUTE, METAB_FAMILY, col = "SITE_METAB") %>%
  filter(grepl("Mayo Clinic", SITE_METAB)) %>%
  select(TISSUE,SITE_METAB,SAMPLE_N,QC_IS_N,QC_PRERUN_N,QC_BLANK_N,
          QC_POOLED_N,QC_REFERENCE_N,QC_DRIFT_N) %>%
  mutate(ALL_SAMPLE_N = SAMPLE_N + QC_IS_N + QC_PRERUN_N + QC_BLANK_N + QC_POOLED_N +
                            QC_REFERENCE_N + QC_DRIFT_N) %>%
  mutate(ALL_SAMPLE_N_D20 = ALL_SAMPLE_N/20) %>% 
  knitr::kable(format = "html") %>%
  scroll_box(width = "100%", height = "200px")
# x %>%
#   select(ALL_SAMPLE_N_D20) %>%
#   mutate(ALL_SAMPLE_N_D20 = ALL_SAMPLE_N_D20 %>% str_split(pattern = '\\.') %>% 
#            map(tail, 1) %>% unlist() %>% as.numeric()) %>%
#   mutate(ALL_SAMPLE_N_D20 = paste0('0.', as.character(ALL_SAMPLE_N_D20)) %>% as.numeric()) %>%
#   unlist() %>%
#   hist(breaks = 100) +
#   xlim(0,1)

# DEV
tissue_study_institute_metab_family <- "plasma_Mayo Clinic_ac"
for(tissue_study_institute_metab_family in tissue_study_institute_metab_families[1]){
  # Variables
  tissue <- tissue_study_institute_metab_family %>% 
    str_split(pattern = '_') %>% unlist() %>% head(n=1)
  study_institute_metab_family <- tissue_study_institute_metab_family %>%
    str_remove(paste0(tissue,'_'))
  named <- 'named'
  
  # Collect the samples (keep QCs) & join sample order
  sample_join <- countdata_df %>%
        ungroup() %>%
        unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
        filter(TISSUE == tissue) %>%
        filter(NAMED == named) %>%
        filter(STUDY_INSTITUTE_METAB_FAMILY == study_institute_metab_family) %>%
        unnest(SAMPLE_DATA) %>%
    select(sample_id, sample_type, sample_order, raw_file)
  
  # Subset Data
################################################################################
  # Collect the samples (remove QCs) & join sample order
p <- countdata_df %>%
    ungroup() %>%
    unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
    filter(TISSUE == tissue) %>%
    filter(NAMED == named) %>%
    filter(STUDY_INSTITUTE_METAB_FAMILY == study_institute_metab_family) %>%
    unnest(COUNT_DATA) %>%
    select(-SAMPLE_DATA) %>%
    left_join(y = sample_join, by = c("viallabel" = "sample_id")) %>%
    select(STUDY_INSTITUTE_METAB_FAMILY,labelid, viallabel, pid, bid,sample_type,sample_order,raw_file) %>%
    unique() %>%
    mutate(alt_sample_order = raw_file %>% str_split(pattern = '_') %>% map(tail, 1) %>% unlist()) %>%
    arrange(raw_file, alt_sample_order)
  p %>%
  knitr::kable(format = "html") %>%
  scroll_box(width = "100%", height = "200px")
}

```

### Determine Which Sites Contain Replicates
  + Ensure that the replicate pairs contain the same labelids
```{r}
# Assign Variables
################################################################################
tissue_study_institute_metab_families <- countdata_df %>%
  ungroup() %>%
  unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
  unite(TISSUE,STUDY_INSTITUTE_METAB_FAMILY, col = TISSUE_STUDY_INSTITUTE_METAB_FAMILY) %>%
  select(TISSUE_STUDY_INSTITUTE_METAB_FAMILY) %>% unlist() %>% as.character() %>% unique()

rep_out_df <- data.frame()
# DEV
# tissue_study_institute_metab_family <- "liver_Mayo Clinic_ac"
for(tissue_study_institute_metab_family in tissue_study_institute_metab_families){
  # Variables
  tissue <- tissue_study_institute_metab_family %>% 
    str_split(pattern = '_') %>% unlist() %>% head(n=1)
  study_institute <- (tissue_study_institute_metab_family %>% 
    str_split(pattern = '_') %>% unlist())[2]
  study_institute_metab_family <- tissue_study_institute_metab_family %>%
    str_remove(paste0(tissue,'_'))
  metab_family <- (study_institute_metab_family %>%
    str_split(pattern = '_') %>% unlist())[2]
  named <- 'named'
  
  # Subset Data
################################################################################
  # Collect the samples (remove QCs) & join sample order
sample_join <- countdata_df %>%
        ungroup() %>%
        unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
        filter(TISSUE == tissue) %>%
        filter(NAMED == named) %>%
        filter(STUDY_INSTITUTE_METAB_FAMILY == study_institute_metab_family) %>%
        unnest(SAMPLE_DATA) %>%
        filter(sample_type == 'Sample') %>%
        select(sample_id, sample_order)
  
  # Determine the number of replicates based on viallabel ending
  reps <- countdata_df %>%
  ungroup() %>%
  unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
  filter(TISSUE == tissue) %>%
  filter(NAMED == named) %>%
  filter(STUDY_INSTITUTE_METAB_FAMILY == study_institute_metab_family) %>%
  unnest(COUNT_DATA) %>%
  filter(viallabel %in% as.character(unlist(sample_join$sample_id))) %>%
    select(viallabel) %>% unlist() %>% as.character() %>% unique() %>%
    str_sub(-3,-1) %>% unique()
  
  if(length(reps) >= 2){
    # Collect number of
    #print(paste0('Number of replicates in ',tissue,' ',study_institute_metab_family,': ', length(reps)))
    #print(paste0('Replicates in ',tissue,' ',study_institute_metab_family,': ', paste(reps, collapse = ' ')))
  
    rep_df <- countdata_df %>%
    ungroup() %>%
    unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
    filter(TISSUE == tissue) %>%
    filter(NAMED == named) %>%
    filter(STUDY_INSTITUTE_METAB_FAMILY == study_institute_metab_family) %>%
    unnest(COUNT_DATA) %>%
    filter(viallabel %in% as.character(unlist(sample_join$sample_id))) %>%
    #left_join(y = sample_join, by = c("viallabel" = "sample_id")) %>%
    unite(labelid, viallabel, col = "labelid_viallabel", remove = F) %>%
    mutate(REPLICATE = case_when(grepl(paste0(reps[1],"$"),labelid_viallabel) ~ reps[1],
                               grepl(paste0(reps[2],"$"),labelid_viallabel) ~ reps[2])) %>%
    select(REPLICATE,labelid_viallabel, labelid, viallabel, pid, bid, METABOLITE_NAME,VALUE)
    
    # rep_summary <- rep_df %>%
    #   mutate(REPLICATE = factor(REPLICATE)) %>%
    #   mutate(labelid_viallabel = factor(labelid_viallabel)) %>%
    #   mutate(labelid = factor(labelid)) %>%
    #   mutate(viallabel = factor(viallabel)) %>%
    #   mutate(pid = factor(pid)) %>%
    #   mutate(bid = factor(bid)) %>%
    #   mutate(METABOLITE_NAME = factor(METABOLITE_NAME)) %>%
    #   select(-VALUE) %>% unique()
    # summary(rep_summary)
    # rep_df %>% select(labelid) %>% table()
    
    r1_v <- rep_df %>%
    filter(REPLICATE == reps[1]) %>%
    select(labelid) %>% unlist() %>% as.character() %>% sort()
    r2_v <- rep_df %>%
    filter(REPLICATE == reps[2]) %>%
    select(labelid) %>% unlist() %>% as.character() %>% sort()
    out_df <- data.frame(TISSUE = tissue, 
               STUDY_INSTITUTE = study_institute, 
               METAB_FAMILY = metab_family,
               NAMED = named,
               REP_N = length(reps),
               REPS = paste(reps, collapse = ';'),
               REP_PAIR_N = sum(r1_v %in% r2_v),
               SAMPLE_N = length(c(r1_v, r2_v)),
               REP_FREQ = sum(r1_v %in% r2_v)*2/length(c(r1_v, r2_v)))
    rep_out_df <- rbind(rep_out_df, out_df)
  }
}
rep_out_df %>%
  arrange(desc(REP_N)) %>% 
  knitr::kable(format = "html") %>%
  scroll_box(width = "100%", height = "200px")
```

##### Subset data to send to Collaborators (Matrices and Dataframes as R Objects)
```{r Subset Replicate Samples for Jun}
# Assign Variables
################################################################################
tissue_study_institute_metab_reps <- countdata_df %>%
  ungroup() %>%
  filter(STUDY_INSTITUTE == 'Mayo Clinic') %>%
  filter(TISSUE %in% c("gastrocnemius","heart","lung","liver","brown-adipose","white-adipose")) %>%
  filter(METAB_FAMILY %in% c('ac','amines','cer','tca')) %>%
  unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
  unite(TISSUE,STUDY_INSTITUTE_METAB_FAMILY, col = TISSUE_STUDY_INSTITUTE_METAB_FAMILY) %>%
  select(TISSUE_STUDY_INSTITUTE_METAB_FAMILY) %>% unlist() %>% as.character() %>% unique()

# DEV
# tissue_study_institute_metab_rep <- "liver_Mayo Clinic_ac"
for(tissue_study_institute_metab_rep in tissue_study_institute_metab_reps){
  # Variables
  tissue <- tissue_study_institute_metab_rep %>% 
    str_split(pattern = '_') %>% unlist() %>% head(n=1)
  study_institute_metab_family <- tissue_study_institute_metab_rep %>%
    str_remove(paste0(tissue,'_'))
  named <- 'named'
  tissue_study_institute_metab_rep_out <- tissue_study_institute_metab_rep %>% 
    str_replace_all('_','-') %>% str_replace_all(' ','-')
  
  # Subset Data
################################################################################
  # Collect the samples (remove QCs) & join sample order
sample_join <- countdata_df %>%
        ungroup() %>%
        unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
        filter(TISSUE == tissue) %>%
        filter(NAMED == named) %>%
        filter(STUDY_INSTITUTE_METAB_FAMILY == study_institute_metab_family) %>%
        unnest(SAMPLE_DATA) %>%
        filter(sample_type == 'Sample') %>%
        select(sample_id, sample_order)
  
  # Collect the metabolites unique to run
  metabolites <- countdata_df %>%
        ungroup() %>%
        unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
        filter(TISSUE == tissue) %>%
        filter(NAMED == named) %>%
        filter(STUDY_INSTITUTE_METAB_FAMILY == study_institute_metab_family) %>%
        unnest(METABOLITE_DATA) %>%
        select(refmet_name) %>% unlist() %>% as.character() %>% unique()
  
  # Determine the number of replicates based on viallabel ending
  reps <- countdata_df %>%
  ungroup() %>%
  unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
  filter(TISSUE == tissue) %>%
  filter(NAMED == named) %>%
  filter(STUDY_INSTITUTE_METAB_FAMILY == study_institute_metab_family) %>%
  unnest(COUNT_DATA) %>%
  filter(viallabel %in% as.character(unlist(sample_join$sample_id))) %>%
    select(viallabel) %>% unlist() %>% as.character() %>% unique() %>%
    str_sub(-3,-1) %>% unique()
  
  
  # Collect abundances in long format and annotate replicate labelids
rep_df <- countdata_df %>%
        ungroup() %>%
        unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
        filter(TISSUE == tissue) %>%
        filter(NAMED == named) %>%
        filter(STUDY_INSTITUTE_METAB_FAMILY == study_institute_metab_family) %>%
        unnest(COUNT_DATA) %>%
        filter(viallabel %in% as.character(unlist(sample_join$sample_id))) %>%
        filter(METABOLITE_NAME %in% metabolites) %>%
        left_join(y = sample_join, by = c("viallabel" = "sample_id")) %>%
        unite(labelid, viallabel, col = "labelid_viallabel", remove = F) %>%
        mutate(REPLICATE = case_when(grepl(paste0(reps[1],"$"),labelid_viallabel) ~ reps[1],
                                     grepl(paste0(reps[2],"$"),labelid_viallabel) ~ reps[2],
                                     grepl(paste0(reps[3],"$"),labelid_viallabel) ~ reps[3]))

# Subset matrices by replicate samples
reps_mats <- rep_df %>%
  unite(labelid, viallabel, col = "labelid_viallabel", remove = F) %>%
  split(.$REPLICATE) %>%
  map(select, labelid_viallabel, METABOLITE_NAME, VALUE) %>%
  map(pivot_wider, names_from = METABOLITE_NAME, values_from = VALUE) %>%
  map(arrange, labelid_viallabel) %>%
  map(column_to_rownames, var = "labelid_viallabel") %>%
  map(as.matrix)
rep_mat1 <- reps_mats[[1]]
rep_mat2 <- reps_mats[[2]]

# Select the replicate orders as dfs
rep_ords <- rep_df %>%
  unite(labelid, viallabel, col = "labelid_viallabel", remove = F) %>%
  split(.$REPLICATE) %>%
  map(select, labelid_viallabel, sample_order) %>%
  map(unique) %>%
  map(arrange, labelid_viallabel)
rep_ord1 <- rep_ords[[1]]
rep_ord2 <- rep_ords[[2]]
x <- (row.names(rep_ord1) %>% str_split(pattern = '_') %>% map(head, n =1)) %>% unlist()
y <- (row.names(rep_ord2) %>% str_split(pattern = '_') %>% map(head, n = 1)) %>% unlist()

# Ensure that samples have the same labelid 
x <- (row.names(rep_mat1) %>% str_split(pattern = '_') %>% map(head, n =1)) %>% unlist()
y <- (row.names(rep_mat2) %>% str_split(pattern = '_') %>% map(head, n = 1)) %>% unlist()
#print(tissue_study_institute_metab_rep)
#print(reps)
#print(table(x == y))
if(all(x == y)){
  # Save the matrices
  mat_file1 <- paste0(WD,'/files_to_share/20201012_replicate-analysis-',tissue_study_institute_metab_rep_out,'-reps1_steep.RDS')
  mat_file2 <- paste0(WD,'/files_to_share/20201012_replicate-analysis-',tissue_study_institute_metab_rep_out,'-reps2_steep.RDS')
  #saveRDS(rep_mat1, mat_file1)
  #saveRDS(rep_mat2, mat_file2)
  # Save the order files
  ord_file1 <- paste0(WD,'/files_to_share/20201012_replicate-analysis-',tissue_study_institute_metab_rep_out,'-reps1-sample-order_steep.RDS')
  ord_file2 <- paste0(WD,'/files_to_share/20201012_replicate-analysis-',tissue_study_institute_metab_rep_out,'-reps2-sample-order_steep.RDS')
  #saveRDS(rep_ord1, ord_file1)
  #saveRDS(rep_ord2, ord_file2)
}

}
```

### Comparison of Samples and Metabolites Between Replicate Pairs (Before and After Normalization)
#### These analyses are rendered in adjunct HTML files in 20200915_metabolomics-pass1a/reports/mayo_clinic

<!-- # ```{r Automation: Boxplots and Density Plots to Measure Normalization, echo=TRUE, fig.show='hide', message=TRUE, warning=TRUE, results='hide'} -->

```{r Automation: Boxplots and Density Plots to Measure Normalization, echo=FALSE, fig.show='hide', message=FALSE, warning=FALSE, results='hide'}
tissue_study_institute_metab_families <- countdata_df %>%
  ungroup() %>%
  filter(STUDY_INSTITUTE == 'Mayo Clinic') %>%
  unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
  unite(TISSUE,STUDY_INSTITUTE_METAB_FAMILY, col = TISSUE_STUDY_INSTITUTE_METAB_FAMILY) %>%
  select(TISSUE_STUDY_INSTITUTE_METAB_FAMILY) %>% unlist() %>% as.character() %>% unique()

# DEV
# tissue_study_institute_metab_family <- "gastrocnemius_Mayo Clinic_amines"
for(tissue_study_institute_metab_family in tissue_study_institute_metab_families){
  
  # Variables
  tissue_study_institute_metab_family_out <- tissue_study_institute_metab_family %>% 
    str_replace_all('_','-') %>% str_replace_all(' ','-')
  tissue <- tissue_study_institute_metab_family %>% 
    str_split(pattern = '_') %>% unlist() %>% head(n=1)
  study_institute_metab_family <- tissue_study_institute_metab_family %>%
    str_remove(paste0(tissue,'_'))
  named <- 'named'
  
  # Collect the samples (remove QCs) & join sample order
  sample_join <- countdata_df %>%
        ungroup() %>%
        unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
        filter(TISSUE == tissue) %>%
        filter(NAMED == named) %>%
        filter(STUDY_INSTITUTE_METAB_FAMILY == study_institute_metab_family) %>%
        unnest(SAMPLE_DATA) %>%
        filter(sample_type == 'Sample') %>%
        select(sample_id, sample_order)

  # Determine the number of replicates based on viallabel ending
  reps <- countdata_df %>%
    ungroup() %>%
    unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
    filter(TISSUE == tissue) %>%
    filter(NAMED == named) %>%
    filter(STUDY_INSTITUTE_METAB_FAMILY == study_institute_metab_family) %>%
    unnest(COUNT_DATA) %>%
    filter(viallabel %in% as.character(unlist(sample_join$sample_id))) %>%
    select(viallabel) %>% unlist() %>% as.character() %>% unique() %>%
    str_sub(-3,-1) %>% unique()
  html_dir = '/Volumes/Frishman_4TB/motrpac/20200915_metabolomics-pass1a/reports/mayo_clinic'
  if((length(reps) == 2) & (tissue %in% c("gastrocnemius","heart","lung","liver","white-adipose"))){
    html_file = paste0("20201012_replicate-analysis-",tissue_study_institute_metab_family_out,'_steep.html')
  rmarkdown::render('/Volumes/Frishman_4TB/motrpac/20200915_metabolomics-pass1a/scripts/20201012_pass1a-metabolomics-mayo-reps-2_steep.Rmd',
    output_format = "html_document",
    output_file = html_file,
    output_dir = html_dir)
    print(paste0('Output File: ', html_file))
  }
}
print(paste0('Output Files PATH: ', html_dir))
```


# Inference:
  + It there are differences in metabolite abundances between the replicates pairs. 
  + We should consider why these samples were replicated.
    + Is it safe to assume these replicate pairs should demonstrate similar metabolite abundances and be correlated?
    + Or, were samples replicated for another reason?




