---
title: | 
 | PASS1A (Rat) Metabolomics: 
 | Feature Removal and Imputation
author: "Alec Steep"
date: "11/01/2020"
always_allow_html: true
output: 
  html_document:
    toc: true
    code_folding: hide
    highlight: zenburn
    css: ../css/style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(cache = FALSE)

# To Render the Markdown, run this line in console
#rmarkdown::render('/Volumes/Frishman_4TB/motrpac/20200915_metabolomics-pass1a/scripts/20201103_pass1a-metabolomics-site-specific-eda_steep.Rmd', output_file = '/Volumes/Frishman_4TB/motrpac/20200915_metabolomics-pass1a/reports/20201103_pass1a-metabolomics-site-specific-eda_steep.html', quiet = TRUE, clean = TRUE)
```

##### CSS Top Styling
```{r CSS Top Styling}
writeLines("td, th { padding : 3px } th { background-color:white; color:black; border:1px solid black; text-align:center } td {color:black; border:1px solid black; word-wrap:break-word; white-space:nowrap; overflow: hidden; text-overflow: ellipsis; max-width:300px; text-align:left}", con= "../css/style.css")

```

## Goals of Analysis
  + Systematically compare shared metabolites and samples across CAS sites

## Analysis

### Setup the Environment
```{r Setup the Environment, message=FALSE, results='hide', warning = FALSE, echo = FALSE}
################################################################################
##### Resources and Dependencies ###############################################
################################################################################

# Set the working directory
#############################################################################
COMP <- "MacBook" 
#COMP <- "GreatLakes"       
if(COMP == "MacBook"){
        # MacBook
        WD <- '/Volumes/Frishman_4TB/motrpac/20200915_metabolomics-pass1a'    
}else if(COMP == "GreatLakes"){
        # MichMed
        WD <- '/home/acsteep/motrpac/20200915_metabolomics-pass1a'
}
rm(COMP)

#setwd(WD)

# Load the dependencies
#source("https://bioconductor.org/biocLite.R")
#BiocManager::install("org.Rn.eg.db")
#install.packages("tidyverse")

# Load dependencies
pacs...man <- c("tidyverse", "data.table","rlang","RColorBrewer","MASS","sfsmisc",
                "pheatmap","caret","ggforce","RANN","kableExtra","gtools","combinat",
                "ggrepel","VIM","mice")
for(pac in pacs...man){
  suppressWarnings(suppressPackageStartupMessages(library(pac, character.only = TRUE)))
}

############################################################
##### Functions ############################################
############################################################

# Name functions
select <- dplyr::select
counts <- DESeq2::counts
map <- purrr::map
desc <- dplyr::desc
arrange <- dplyr::arrange
melt <- reshape2::melt
mutate <- dplyr::mutate

# Global options
options(dplyr.print_max = 100)
options(scipen=10000)

# Source the functions
source(paste0(WD,'/functions/not_in.R'))
source(paste0(WD,'/functions/rat_mouse_ortho.R'))
source(paste0(WD,'/functions/mouse2rat_ortho.R'))
source(paste0(WD,'/functions/lmp.R'))
source(paste0(WD,'/functions/cor_PC_1_6.R'))
source(paste0(WD,'/functions/elbow_finder.R'))
source(paste0(WD,'/functions/cor_outlier2.R'))
source(paste0(WD,'/functions/DissimilarityMatrixNominal.R'))
source(paste0(WD,'/functions/lm_eqn.R'))
source(paste0(WD,'/functions/reorder_cormat.R'))
source(paste0(WD,'/functions/save_pheatmap_pdf.R'))
source(paste0(WD,'/functions/modeav.R'))
source(paste0(WD,'/functions/count_na.R'))
source(paste0(WD,'/functions/se_mean.R'))
source(paste0(WD,'/functions/Mode.R'))
source(paste0(WD,'/functions/NumericSummaryStats.R'))
source(paste0(WD,'/functions/AutoScaleMatrix.R'))
source(paste0(WD,'/functions/ReverseAutoScaleMatrix.R'))
source(paste0(WD,'/functions/CenterMatrix.R'))
source(paste0(WD,'/functions/RangeScaleMatrix.R'))
source(paste0(WD,'/functions/ParetoScaleMatrix.R'))
source(paste0(WD,'/functions/VastScaleMatrix.R'))
source(paste0(WD,'/functions/LevelScaleMatrix.R'))
source(paste0(WD,'/functions/Log10Matrix.R'))
source(paste0(WD,'/functions/PowerMatrix.R'))

```

### Dataset
```{r Dataset Data Format}
print(descriptor)

```


### Zero/Missing Values in Metabolites
-Note: TODO: Adjust script to account for Emory

```{r Zero/Missing Values in Metabolites}
if(site != 'Emory University'){
# Identify Zero/Missing Values in Metabolites
################################################################################
  
  # Variables
  ##################
  # Min values (that isn't zero)
  min_val <- dataset_df$VALUE[dataset_df$VALUE != 0] %>% min(na.rm = T)
  # Samples
  sams <- dataset_df %>%
    filter(!is.na(labelid)) %>%
    select(labelid) %>% unlist() %>% unique()
  
  na_df <- dataset_df %>%
    ungroup() %>% 
    filter(!is.na(labelid)) %>%
    mutate(ZERO_LOG = ifelse(VALUE == 0, 1, 0)) %>%
    mutate(NA_LOG = ifelse(is.na(VALUE), 1, 0)) %>%
    group_by(METABOLITE_NAME) %>%
    mutate(MIN = VALUE[VALUE != 0] %>% min(na.rm = T)) %>%
    mutate(MAX = VALUE[VALUE != 0] %>% max(na.rm = T)) %>%
    mutate(MEAN = VALUE[VALUE != 0] %>% mean(na.rm = T)) %>%
    mutate(MEDIAN = VALUE[VALUE != 0] %>% median(na.rm = T)) %>%
    mutate(Q1 = quantile(VALUE[VALUE != 0], na.rm = TRUE, probs = 0.25) %>% round(digits = 2)) %>%
    mutate(Q3 = quantile(VALUE[VALUE != 0], na.rm = TRUE, probs = 0.75) %>% round(digits = 2)) %>%
    mutate(ZERO_N = sum(ZERO_LOG, na.rm = T)) %>%
    mutate(ZERO_FREQ = round(ZERO_N/length(sams), digits = 2)) %>%
    mutate(NA_N = sum(NA_LOG, na.rm = T)) %>%
    mutate(NA_FREQ = round(NA_N/length(sams), digits = 2)) %>%
    select(DATASET,TISSUE,STUDY_INSTITUTE,METAB_FAMILY,CH_CHROMATOGRAPHY_TYPE,
           MS_TYPE,MS_ION_MODE,METABOLITE_NAME, ZERO_N, ZERO_FREQ, NA_N, NA_FREQ,
           MIN,Q1,MEDIAN,Q3,MAX) %>%
    unique() %>%
    arrange(desc(NA_FREQ), desc(ZERO_FREQ)) %>%
    ungroup()
  
  # Visualize the results
  ################
  na_df %>%
    filter(!(ZERO_N == 0 & NA_N == 0)) %>%
    select(METABOLITE_NAME, ZERO_FREQ ,NA_FREQ) 
}
```
### Zero/Missing Values in Samples
-Note: TODO: Adjust script to account for Emory

```{r Zero/Missing Values in Metabolites}
if(site != 'Emory University'){
# Identify Zero/Missing Values in Metabolites
################################################################################
  
  # Variables
  ##################
  # Min values (that isn't zero)
  min_val <- dataset_df$VALUE[dataset_df$VALUE != 0] %>% min(na.rm = T)
  # Samples
  sams <- dataset_df %>%
    filter(!is.na(labelid)) %>%
    select(labelid) %>% unlist() %>% unique()
  
  sample_na_df <- dataset_df %>%
    ungroup() %>% 
    filter(!is.na(labelid)) %>%
    mutate(ZERO_LOG = ifelse(VALUE == 0, 1, 0)) %>%
    mutate(NA_LOG = ifelse(is.na(VALUE), 1, 0)) %>%
    group_by(labelid) %>%
    mutate(MIN = VALUE[VALUE != 0] %>% min(na.rm = T)) %>%
    mutate(MAX = VALUE[VALUE != 0] %>% max(na.rm = T)) %>%
    mutate(MEAN = VALUE[VALUE != 0] %>% mean(na.rm = T)) %>%
    mutate(MEDIAN = VALUE[VALUE != 0] %>% median(na.rm = T)) %>%
    mutate(Q1 = quantile(VALUE[VALUE != 0], na.rm = TRUE, probs = 0.25) %>% round(digits = 2)) %>%
    mutate(Q3 = quantile(VALUE[VALUE != 0], na.rm = TRUE, probs = 0.75) %>% round(digits = 2)) %>%
    mutate(ZERO_N = sum(ZERO_LOG, na.rm = T)) %>%
    mutate(ZERO_FREQ = round(ZERO_N/length(sams), digits = 2)) %>%
    mutate(NA_N = sum(NA_LOG, na.rm = T)) %>%
    mutate(NA_FREQ = round(NA_N/length(sams), digits = 2)) %>%
    select(DATASET,TISSUE,STUDY_INSTITUTE,METAB_FAMILY,CH_CHROMATOGRAPHY_TYPE,
           MS_TYPE,MS_ION_MODE,labelid, ZERO_N, ZERO_FREQ, NA_N, NA_FREQ,
           MIN,Q1,MEDIAN,Q3,MAX) %>%
    unique() %>%
    arrange(desc(NA_FREQ), desc(ZERO_FREQ)) %>%
    ungroup()
  
  # Visualize the results
  ################
  sample_na_df %>%
    filter(!(ZERO_N == 0 & NA_N == 0)) %>%
    select(labelid, ZERO_FREQ ,NA_FREQ) 
}
```

### Examine Boxplot of All Metabolites
```{r Examine Boxplot of all Metabolites}
# Variables
###############
join_df <- na_df %>%
  select(METABOLITE_NAME,ZERO_N,ZERO_FREQ,NA_N,NA_FREQ)
miss_mets <- na_df %>%
  filter(ZERO_FREQ > 0) %>%
  select(METABOLITE_NAME) %>% unique() %>% unlist() %>% as.character()
na_mets <- na_df %>%
  filter(NA_FREQ > 0) %>%
  select(METABOLITE_NAME) %>% unique() %>% unlist() %>% as.character()

# Plot Boxplots (with high abundance metabolites)
#########################################
if(sum(na_df$ZERO_FREQ) > 0){
  # Variables
  ZERO_Q1 <- na_df %>%
    filter(ZERO_FREQ > 0) %>%
    select(Q1) %>% unlist() %>% as.numeric() %>%
    median(na.rm = T)
  # Raw (Zero)
  p <- dataset_df %>%
    left_join(y = join_df, by = 'METABOLITE_NAME') %>%
    ggplot(aes(y = VALUE, x = METABOLITE_NAME, color = ZERO_FREQ)) +
    geom_boxplot(alpha = 0.8) +
    labs(title= "Original", y = "Abundance", x = "") +
    theme(axis.text.x = element_text(size = 5, angle = 90)) +
    theme(legend.text = element_text(size=8),
        legend.title = element_text(size = 7))
  plot(p)

  # Raw
  p <- dataset_df %>%
    left_join(y = join_df, by = 'METABOLITE_NAME') %>%
    ggplot(aes(y = VALUE, x = METABOLITE_NAME, color = ZERO_FREQ)) +
    geom_boxplot(alpha = 0.8) +
    labs(title= "Original: Truncated", y = "Abundance", x = "") +
    ylim(0,ZERO_Q1)+
    theme(axis.text.x = element_text(size = 5, angle = 90)) +
    theme(legend.text = element_text(size=8),
        legend.title = element_text(size = 7))
  plot(p)
}

if(sum(na_df$NA_FREQ) > 0){
  # Variables
  NA_Q1 <- na_df %>%
    filter(NA_FREQ > 0) %>%
    select(Q1) %>% unlist() %>% as.numeric() %>%
    median(na.rm = T)
  
  # Raw (NA)
  p <- dataset_df %>%
    left_join(y = join_df, by = 'METABOLITE_NAME') %>%
    mutate(NA_LAB = ifelse(NA_FREQ>0, METABOLITE_NAME, '')) %>%
    ggplot(aes(y = VALUE, x = METABOLITE_NAME, color = NA_LAB)) +
    geom_boxplot(alpha = 0.8) +
    labs(title= "Original", y = "Abundance", x = "") +
    theme(axis.text.x = element_text(size = 5, angle = 90)) +
    theme(legend.text = element_text(size=8),
        legend.title = element_text(size = 7))
  plot(p)
  # Truncated
  p <- dataset_df %>%
    left_join(y = join_df, by = 'METABOLITE_NAME') %>%
    mutate(NA_LAB = ifelse(NA_FREQ>0, METABOLITE_NAME, '')) %>%
    ggplot(aes(y = VALUE, x = METABOLITE_NAME, color = NA_LAB)) +
    geom_boxplot(alpha = 0.8) +
    labs(title= "Original: Truncated", y = "Abundance", x = "") +
    ylim(0,median(na_df$Q1, na.rm = T))+
    theme(axis.text.x = element_text(size = 5, angle = 90)) +
    theme(legend.text = element_text(size=8),
        legend.title = element_text(size = 7))
  plot(p)
  # Just the NA mets, truncated
  # Truncated
  p <- dataset_df %>%
    filter(METABOLITE_NAME %in% na_mets) %>%
    left_join(y = join_df, by = 'METABOLITE_NAME') %>%
    ggplot(aes(y = VALUE, x = METABOLITE_NAME, color = NA_N)) +
    geom_boxplot(alpha = 0.8) +
    labs(title= "Original: Truncated", y = "Abundance", x = "") +
    ylim(0,NA_Q1)+
    theme(axis.text.x = element_text(size = 5, angle = 90)) +
    theme(legend.text = element_text(size=8),
        legend.title = element_text(size = 7))
  plot(p)
}

```

### Scatterplots of Metabolites with Missing Values
```{r Scatterplots of Metabolites with Missing Values}
# Variables
################
miss_mets <- na_df %>%
  filter(ZERO_FREQ > 0.5) %>%
  select(METABOLITE_NAME) %>% unique() %>% unlist() %>% as.character()
na_mets <- na_df %>%
  filter(NA_FREQ > 0) %>%
  select(METABOLITE_NAME) %>% unique() %>% unlist() %>% as.character()
plot_df <- dataset_df %>%
  filter(!is.na(labelid)) %>%
    left_join(y = pheno_df, by = "viallabel")

# DEV
################
#met <- miss_mets[1]
#met <- na_mets[1]

for(met in c(na_mets,miss_mets)){
  # Variables
  M_Q1 <- na_df %>%
    filter(METABOLITE_NAME == met) %>%
    select(Q1) %>% unlist() %>% as.numeric() %>%
    median(na.rm = T)
  # Examine biological features
  p <- plot_df %>%
    filter(METABOLITE_NAME == met) %>%
    mutate(Key.anirandgroup = factor(Key.anirandgroup, levels = ec_levels)) %>%
    ggplot(aes(x = Key.anirandgroup, y = VALUE, color = Key.anirandgroup)) +
    geom_boxplot() +
    geom_jitter(height = 0) +
    ggtitle(met) +
    scale_color_manual(values=ec_colors) +
    theme(axis.text.x = element_text(size = 10, angle = 90)) +
    theme(aspect.ratio=1)
  plot(p)
  p1 <- plot_df %>%
    filter(METABOLITE_NAME == met) %>%
    mutate(Key.anirandgroup = factor(Key.anirandgroup, levels = ec_levels)) %>%
    ggplot(aes(x = Key.anirandgroup, y = VALUE, color = Key.anirandgroup)) +
    geom_boxplot() +
    geom_jitter(data = filter(plot_df,METABOLITE_NAME == met), 
                aes(Key.anirandgroup, y = VALUE), height = 0) +
    ggtitle(paste0(met," Truncated")) +
    ylim(0,M_Q1) +
    scale_color_manual(values=ec_colors) +
    theme(axis.text.x = element_text(size = 10, angle = 90)) +
    theme(aspect.ratio=1)
  plot(p1)
  p2 <- plot_df %>%
    filter(METABOLITE_NAME == met) %>%
    mutate(Registration.sex = factor(Registration.sex)) %>%
    ggplot(aes(x = Registration.sex, y = VALUE, color = Registration.sex)) +
    geom_boxplot() +
    geom_jitter(height = 0) +
    ggtitle(met) +
    theme(aspect.ratio=1)
  plot(p2)
}


```

### Determine Which Values Corrlate most with Metabolites with Missing Values

### 
```{r Determine Which Values Corrlate most with Metabolites with Missing Values}


# Generate a histogram of features with zero values
na_df %>%
  ggplot(aes(x = ZERO_FREQ)) +
  geom_histogram() +
  geom_density() +
  xlim(0,1)

# Generate a histogram of features with missing values
na_df %>%
  ggplot(aes(x = NA_FREQ)) +
  geom_histogram() +
  geom_density() +
  xlim(0,1)


features_removed <- na_df %>%
  filter(NA_FREQ >= 0.75) %>%
  select(METABOLITE_NAME) %>% unlist() %>% as.character()
features_removed
# Print features removed


```

### Collect Correlation Values Between Features
```{r}
# Variables
################
# Select the metabolite to impute
imp_mets <- na_df %>%
  filter(NA_FREQ > 0) %>%
  arrange(NA_FREQ) %>%
  select(METABOLITE_NAME) %>% unique() %>% unlist() %>% as.character()
# Remove the samples with missing values
plot_df <- dataset_df %>%
  filter(METABOLITE_NAME %!in% features_removed) %>%
  filter(!is.na(labelid)) %>%
  select(METABOLITE_NAME, viallabel,VALUE) %>%
  mutate(VALUE = as.numeric(VALUE)) %>%
  pivot_wider(names_from = METABOLITE_NAME, values_from = VALUE)
# Convert data to matrix
plot_mat <- dataset_df %>%
  filter(METABOLITE_NAME %!in% features_removed) %>%
  #replace_na(list(VALUE = 0)) %>%
  filter(!is.na(labelid)) %>%
  select(METABOLITE_NAME, viallabel,VALUE) %>%
  mutate(VALUE = as.numeric(VALUE)) %>%
  pivot_wider(names_from = METABOLITE_NAME, values_from = VALUE) %>%
  tibble::column_to_rownames(var = "viallabel") %>%
  as.matrix()

# Create correlation matrix
###########################
Corr <- 'Pearson'
#Corr <- 'Spearman'
# Create an PxP Matrix of correlation
if(Corr == 'Pearson'){
        cor1 <- stats::cor(plot_mat, method = 'pearson', use = "pairwise.complete.obs") %>% round(digits = 3)
}else if(Corr == 'Spearman'){
        cor1 <- stats::cor(plot_mat, method = 'spearman') %>% round(digits = 3)
}

# Orient the colors and breaks
paletteLength <- 1000
myColor <- colorRampPalette(c("blue", "white", "red"))(paletteLength)
# length(breaks) == length(paletteLength) + 1
# use floor and ceiling to deal with even/odd length pallettelengths
myBreaks <- c(seq(-1, 0, length.out=ceiling(paletteLength/2) + 1), 
              seq(1/paletteLength, 1, length.out=floor(paletteLength/2)))

# Plot the heatmap
p1 <- pheatmap(cor1, color=myColor, breaks=myBreaks,
              main = descriptor,
              cluster_rows = T, cluster_cols = T,fontsize = 8,
              show_rownames = F, show_colnames = F,
              legend = F, drop_levels = F)

```

### Impute Values with KNN imputation
```{r Impute Values}
# if(descriptor == "BroadInstitute-hippocampus-hilicpos-HILIC-ESI-positive-named-untargeted" &
#    met == "Atenolol"){
#   outlier = T
# }else{
#      outlier = F
#    }
# Find the features most correlated with the metabolite with the least NA values to the most
##########################
# Save the correlation matrix values values
# DEV
#################
#met <- imp_mets[1]
#cm <- corr_mets[1]
outlier = F
imp_list <- list()
out_list <- list()
mice_df <- plot_df
imp_mets <- imp_mets[imp_mets %!in% features_removed]
for(met in imp_mets[1]){
  corr_vals <- cor1[met,(names(cor1[met,]) != met)] %>% sort() %>% rev()
  corr_mets <- names(corr_vals > 0.5)[1:4]
  # Samples with missing values
  miss_sams <- plot_df %>%
    filter(is.na(!!sym(met))) %>%
    select(viallabel) %>% unlist() %>% as.character()
  # Collect the original matrix
  mat_org <- plot_df %>% 
    select(-imp_mets[imp_mets != met]) %>%
    select(-viallabel) %>%
    as.matrix()
  # Original rownames
  rownames_org <- plot_df$viallabel
  # Scale the original matrix
  imp_mat <- plot_df %>%
    select(-imp_mets[imp_mets != met]) %>% 
    select(-viallabel) %>%
    as.matrix() %>% AutoScaleMatrix()
  
  # Use a knn method to impute missing values (need to come back and adjust)
  preProcValues <- preProcess(imp_mat,
                              method = c("knnImpute"),
                            k = 9,
                            knnSummary = mean)
  
  # To get the normalizaed data
  imp_mat <- predict(preProcValues, imp_mat, na.action = na.pass)
  
  # Revert back
  imp_df <- data.frame(ReverseAutoScaleMatrix(mat_org = mat_org, mat_norm = imp_mat)[,met])
  names(imp_df) <- met
  out_list <- c(out_list, imp_df)
  
   # Visualize the values from missing metabolite
  print(met)
  print("Missing Values:")
  plot_df[[met]] %>% print()
  print("Imputed Results:")
  imp_df[[met]][is.na(plot_df[[met]])] %>% print()
  
  # Generate margin plots
  for(cm in corr_mets){
    max_val <- max(as.numeric(unlist(plot_df[[met]])), na.rm = T)
    if(outlier){
      marg_df <- plot_df
      marg_df[[met]] <- c(plot_df[[met]][plot_df[[met]] != max_val],NA)
      marginplot(marg_df[, c(met, cm)], 
               col = mdc(1:2), cex = 1.2,
               cex.lab = 1.2, cex.numbers = 1.3, pch = 19)
    }else(
      marginplot(plot_df[, c(met, cm)], 
               col = mdc(1:2), cex = 1.2,
               cex.lab = 1.2, cex.numbers = 1.3, pch = 19)
    )
  }
  for(cm in corr_mets){
  # Plot imputed values
      marg_plot <- cbind(imp_df,plot_df[,cm])
      marginplot(marg_plot, 
               col = mdc(1:2), cex = 1.2,
               cex.lab = 1.2, cex.numbers = 1.3, pch = 19)
  }
  
# PCA: Post-Imputation
#################
pca <- prcomp(na.omit(imp_mat), scale. = F)
percentVar <- pca$sdev^2/sum(pca$sdev^2)
PC <- pca$x %>% as.data.frame()
#PC$METABOLITE <- as.character(row.names(pca$x))
PC$viallabel <- rownames_org
PC <- PC %>%
  mutate(NA_SAM = ifelse(viallabel %in% miss_sams, '1', '0'))

p0 <- PC %>%
  ggplot(aes(x = PC1, y = PC2, color = NA_SAM)) +
  geom_point(size = 3) +
  #geom_text_repel(aes(label = viallabel))
  ggtitle(paste0(met,': Shared Samples and Metabolites')) +
  xlab(paste0('PC1: ',round(percentVar[1]*100,2),'% variance')) +
  ylab(paste0('PC2: ',round(percentVar[2]*100,2),'% variance')) +
  theme(aspect.ratio=1)
plot(p0)
  
  # Compare your imputation with that from mice
  ########################
  # clean_names[grepl("1",clean_names)]
  #  dirty_names <- colnames(mat_org)
  # clean_names <- dirty_names %>%
  #   str_remove_all(' ') %>%
  #   str_remove_all('/') %>%
  #   str_remove_all('-') %>%
  #   str_remove_all(',') %>%
  #   str_replace_all('0','a') %>%
  #   str_replace_all('1','b') %>%
  #   str_replace_all('2','c') %>%
  #   str_replace_all('3','d') %>%
  #   str_replace_all('4','e') %>%
  #   str_replace_all('5','f') %>%
  #   str_replace_all('6','g') %>%
  #   str_replace_all('7','h') %>%
  #   str_replace_all('8','i') %>%
  #   str_replace_all('9','j') %>%
  #   str_replace_all(':','_') %>%
  #   str_replace_all("\\)",'_') %>%
  #   str_replace_all("\\(",'_') %>%
  #   str_replace_all("\\]",'_') %>%
  #   str_replace_all("\\[",'_')
  # 
  #  colnames(mat_org) <- clean_names
  #  mice_df <- mat_org
  #  plot_imp_df <- mice(mice_df, seed = 123)
  #  summary(plot_imp_df)
  #  complete(plot_imp_df, action=1)

}
out_df <- data.frame(out_list, check.names = F)
#out_df

```

```{r Low Imputation Values}
 na_df %>%
    filter(METABOLITE_NAME == "CAR(20:0)")
```


### Documentation of Imputation Method and Predictors
```{r}

# Demonstrate how well knn worked for each metabolite






```





## Session Info
```{r Sesh}
session_info()
```