---
title: | 
 | PASS1A (Rat) Metabolomics: 
 | Visualize Dimensions from Site Specific Analysis
author: "Alec Steep"
date: "12/17/2020"
always_allow_html: true
output: 
  html_document:
    toc: true
    code_folding: hide
    highlight: zenburn
    css: ../css/style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(cache = FALSE)

# To Render the Markdown, run this line in console
#rmarkdown::render('/Volumes/Frishman_4TB/motrpac/20200915_metabolomics-pass1a/scripts/20201103_pass1a-metabolomics-site-specific-eda_steep.Rmd', output_file = '/Volumes/Frishman_4TB/motrpac/20200915_metabolomics-pass1a/reports/20201103_pass1a-metabolomics-site-specific-eda_steep.html', quiet = TRUE, clean = TRUE)
```

##### CSS Top Styling
```{r CSS Top Styling}
writeLines("td, th { padding : 3px } th { background-color:white; color:black; border:1px solid black; text-align:center } td {color:black; border:1px solid black; word-wrap:break-word; white-space:nowrap; overflow: hidden; text-overflow: ellipsis; max-width:300px; text-align:left}", con= "../css/style.css")

```

## Goals of Analysis
  + TODO

## Analysis

### Setup the Environment (Top)
```{r Setup the Environment (Top), message=FALSE, results='hide', warning = FALSE, echo = FALSE}
################################################################################
##### Resources and Dependencies ###############################################
################################################################################

# Set the working directory
#############################################################################
COMP <- "MacBook" 
#COMP <- "GreatLakes"       
if(COMP == "MacBook"){
        # MacBook
        WD <- '/Volumes/Frishman_4TB/motrpac/20200915_metabolomics-pass1a'    
}else if(COMP == "GreatLakes"){
        # MichMed
        WD <- '/home/acsteep/motrpac/20200915_metabolomics-pass1a'
}

#setwd(WD)

# Load the dependencies
#source("https://bioconductor.org/biocLite.R")
#BiocManager::install("org.Rn.eg.db")
#install.packages("kableExtra")

# Load dependencies
pacs...man <- c("tidyverse","ggrepel","data.table","rlang","RColorBrewer","MASS","sfsmisc",
                "pheatmap","caret","ggforce","RANN","kableExtra","gtools","combinat",
                "gridExtra")
for(pac in pacs...man){
  suppressWarnings(suppressPackageStartupMessages(library(pac, character.only = TRUE)))
}

############################################################
##### Functions ############################################
############################################################

# Name functions
select <- dplyr::select
counts <- DESeq2::counts
map <- purrr::map
desc <- dplyr::desc
arrange <- dplyr::arrange
melt <- reshape2::melt
mutate <- dplyr::mutate

# Global options
options(dplyr.print_max = 100)
options(scipen=10000)

# Source the functions
source(paste0(WD,'/functions/not_in.R'))
source(paste0(WD,'/functions/rat_mouse_ortho.R'))
source(paste0(WD,'/functions/mouse2rat_ortho.R'))
source(paste0(WD,'/functions/lmp.R'))
source(paste0(WD,'/functions/cor_PC_1_6.R'))
source(paste0(WD,'/functions/elbow_finder.R'))
source(paste0(WD,'/functions/cor_outlier2.R'))
source(paste0(WD,'/functions/DissimilarityMatrixNominal.R'))
source(paste0(WD,'/functions/lm_eqn.R'))
source(paste0(WD,'/functions/reorder_cormat.R'))
source(paste0(WD,'/functions/save_pheatmap_pdf.R'))
source(paste0(WD,'/functions/modeav.R'))
source(paste0(WD,'/functions/count_na.R'))
source(paste0(WD,'/functions/se_mean.R'))
source(paste0(WD,'/functions/Mode.R'))
source(paste0(WD,'/functions/NumericSummaryStats.R'))
source(paste0(WD,'/functions/AutoScaleMatrix.R'))
source(paste0(WD,'/functions/ReverseAutoScaleMatrix.R'))
source(paste0(WD,'/functions/CenterMatrix.R'))
source(paste0(WD,'/functions/RangeScaleMatrix.R'))
source(paste0(WD,'/functions/ParetoScaleMatrix.R'))
source(paste0(WD,'/functions/VastScaleMatrix.R'))
source(paste0(WD,'/functions/LevelScaleMatrix.R'))
source(paste0(WD,'/functions/Log10Matrix.R'))
source(paste0(WD,'/functions/PowerMatrix.R'))

```

### Development Variables
```{r Development Variables}
save_tf <- T
```


### Load the Data
```{r Load Count Data & MetaData}
# Load the Data
################################################################################
# Files
metadata_rds <- paste0(WD, '/data/20201010_pass1a-metabolomics-metadata-table_steep.rds')
# Load Data
metadata_df <- readRDS(file = metadata_rds)

# Start the clock
#ptm <- proc.time()

# Takes 21+ seconds (881.6 Mb) 1073+ seconds for (7.5Gb)
countdata_rds <- paste0(WD, '/data/20201010_pass1a-metabolomics-countdata-nested_steep.rds')
# Load the data
countdata_df <- readRDS(file = countdata_rds)

# Stop the clock
#proc.time() - ptm
```

### Metadata
```{r Metadata Format}
metadata_df %>%
  head %>% 
  knitr::kable(format = "html") %>%
  scroll_box(width = "100%", height = "200px")
```

### Count Data
```{r Count Data Format}
countdata_df %>%
  head %>%
  knitr::kable(format = "html") %>%
  scroll_box(width = "100%", height = "200px")
```

### Load, Incorporate, & Display Phenotype Data
```{r Incorporate Phenotype Data, results='asis'}
# Load the phenotype data
pheno_obj <- paste0(WD,"/data/20201021_pass1a-06-pheno-viallabel_steep.rds")
pheno_df <- readRDS(pheno_obj)

# Set a vector for Exercise/Control Levels and Colors
ec_levels <- c('Exercise - IPE',
               'Exercise - 0.5 hr',
               'Exercise - 1 hr',
               'Exercise - 4 hr',
               'Exercise - 7 hr',
               'Exercise - 24 hr',
               'Exercise - 48 hr',
               'Control - IPE',
               'Control - 7 hr')
ec_colors <- c('gold',
               'darkgoldenrod1',
               'orange',
               'darkorange',
               'darkorange2',
               'darkorange3',
               'darkorange4',
               'steelblue1',
               'steelblue4')

pheno_df %>%
  head(n = 20) %>% 
  knitr::kable(format = "html") %>%
  scroll_box(width = "100%", height = "200px")
```

### Quantify of Samples and Metabolites Across "Named" Batches
```{r Named Samples and Metabolites Across Sites, Technologies, & Tissues}

# Order of Sites and metab_family
site_metab_order <- metadata_df %>%
  unite(STUDY_INSTITUTE, METAB_FAMILY, col = "SITE_METAB") %>%
  select(TISSUE,SITE_METAB,SAMPLE_N,QC_IS_N,QC_PRERUN_N,QC_BLANK_N,
          QC_POOLED_N,QC_REFERENCE_N,QC_DRIFT_N,METABOLITE_N) %>%
  group_by(SITE_METAB) %>%
  select(SITE_METAB,SAMPLE_N) %>%
  mutate(SAMPLE_SUM = sum(SAMPLE_N)) %>%
  select(SITE_METAB, SAMPLE_SUM) %>%
  arrange(desc(SAMPLE_SUM)) %>% unique() %>%
  select(SITE_METAB) %>% unlist() %>% as.character() %>% unique()

# Order of tissues
tissue_order <- metadata_df %>%
  unite(STUDY_INSTITUTE, METAB_FAMILY, col = "SITE_METAB") %>%
  select(TISSUE,SITE_METAB,SAMPLE_N,QC_IS_N,QC_PRERUN_N,QC_BLANK_N,
          QC_POOLED_N,QC_REFERENCE_N,QC_DRIFT_N,METABOLITE_N) %>%
  group_by(TISSUE) %>%
  mutate(SAMPLE_SUM = sum(SAMPLE_N)) %>%
  select(TISSUE, SAMPLE_SUM) %>%
  arrange(desc(SAMPLE_SUM)) %>% unique() %>%
  select(TISSUE) %>% unlist() %>% as.character() %>% unique() %>% rev()
  
# Create a plot of sample number by tissue and technology
metadata_df %>%
  unite(STUDY_INSTITUTE, METAB_FAMILY, col = "SITE_METAB") %>%
  select(TISSUE,SITE_METAB,SAMPLE_N,QC_IS_N,QC_PRERUN_N,QC_BLANK_N,
          QC_POOLED_N,QC_REFERENCE_N,QC_DRIFT_N,METABOLITE_N) %>%
  mutate(TISSUE = factor(TISSUE, levels = tissue_order)) %>%
  mutate(SITE_METAB = factor(SITE_METAB, levels = site_metab_order)) %>%
  ggplot(aes(SITE_METAB,TISSUE)) +
    geom_tile(aes(fill = SAMPLE_N)) + 
    geom_text(aes(label = SAMPLE_N)) +
    scale_fill_gradient(low = "white", high = "red") +
  ggtitle("Samples Across Named Runs") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.title.x = element_blank(),
  axis.title.y = element_blank()) +
  theme(legend.position = "none") +
  scale_x_discrete(position = "top") +
  theme(axis.text.x = element_text(angle = 300, hjust = 0.9))

# METABOLITE_NAMED_N
# Create a plot of sample number by tissue and technology
metadata_df %>%
  unite(STUDY_INSTITUTE, METAB_FAMILY, col = "SITE_METAB") %>%
  select(TISSUE,NAMED,SITE_METAB,SAMPLE_N,QC_IS_N,QC_PRERUN_N,QC_BLANK_N,
          QC_POOLED_N,QC_REFERENCE_N,QC_DRIFT_N,METABOLITE_N) %>%
  mutate(TISSUE = factor(TISSUE, levels = tissue_order)) %>%
  mutate(SITE_METAB = factor(SITE_METAB, levels = site_metab_order)) %>%
  filter(NAMED == 'named') %>%
  mutate(METABOLITE_NAMED_N = 0) %>%
  mutate(METABOLITE_NAMED_N = ifelse(NAMED == 'named', METABOLITE_N, METABOLITE_NAMED_N)) %>%
  ggplot(aes(SITE_METAB,TISSUE)) +
    geom_tile(aes(fill = METABOLITE_NAMED_N)) + 
    geom_text(aes(label = METABOLITE_NAMED_N)) +
    scale_fill_gradient(low = "white", high = "red") +
  ggtitle("Named Metabolites Across Runs") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.title.x = element_blank(),
  axis.title.y = element_blank()) +
  theme(legend.position = "none") +
  scale_x_discrete(position = "top") +
  theme(axis.text.x = element_text(angle = 300, hjust = 0.9))

```

### Shared Metabolites and Samples
```{r Shared Metabolites and Samples}
shared_casrun_file <- paste0(WD, '/data/20201103_shared-samples-metabs-sites-runs_steep.RDS')
df_shared_casrun <- readRDS(file = shared_casrun_file)

#Broad Institute_hilicpos;University of Michigan_rppos
#Duke University_ac;Broad Institute_hilicpos
#Duke University_ac;University of Michigan_rppos

# df_shared_casrun %>%
#   knitr::kable(format = "html") %>%
#   scroll_box(width = "100%", height = "200px")
df_shared_casrun <- df_shared_casrun %>%
  arrange(desc(METABOLITES_N_RUN)) %>%
  filter(METABOLITES_N_RUN >= 2) %>%
  filter(SAMPLES_N_RUN >= 2) %>%
  mutate(COMP_ID = str_pad(row_number(), 4, pad = "0"))
# df_shared_casrun %>%
#   knitr::kable(format = "html") %>%
#   scroll_box(width = "100%", height = "200px")
df_shared_casrun
```

### Visualize the Major Dimensions of the Metabolomics Pass1a (6mo) Hypercube
``` {r Visualize the Major Dimensions of the Metabolomics Pass1a (6mo) Hypercube}
# Collect the dataframe for plotting
df <- metadata_df %>%
  select(DATASET,NAMED,TISSUE,STUDY_INSTITUTE,CH_CHROMATOGRAPHY_TYPE,MS_TYPE,MS_ION_MODE,METAB_FAMILY) %>%
  unite(CH_CHROMATOGRAPHY_TYPE,MS_TYPE,MS_ION_MODE, col = "TECHNOLOGY")
# Collect order of factors for variables
dataset_levels <- df$DATASET %>% table() %>% sort() %>% names()
named_levels <- df$NAMED %>% table() %>% sort() %>% rev() %>% names()
tissue_levels <- df$TISSUE %>% table() %>% sort() %>% rev() %>% names()
institute_levels <- df$STUDY_INSTITUTE %>% table() %>% sort() %>% rev() %>% names()
technology_levels <- df$TECHNOLOGY %>% table() %>% sort() %>% rev() %>% names()
metab_family_levels <- df$METAB_FAMILY %>% table() %>% sort() %>% rev() %>% names()
# Arrange dataframe
df <- df %>%
  mutate(DATASET = factor(DATASET, levels = dataset_levels)) %>%
  mutate(NAMED = factor(NAMED, levels = named_levels)) %>%
  mutate(TISSUE = factor(TISSUE, levels = tissue_levels)) %>%
  mutate(STUDY_INSTITUTE = factor(STUDY_INSTITUTE, levels = institute_levels)) %>%
  mutate(TECHNOLOGY = factor(TECHNOLOGY, levels = technology_levels)) %>%
  mutate(METAB_FAMILY = factor(METAB_FAMILY, levels = metab_family_levels)) %>%
  arrange(TISSUE,STUDY_INSTITUTE,TECHNOLOGY,METAB_FAMILY,DATASET,NAMED)
df$ORDER <- row.names(df) %>% as.numeric()

plot_df <- df %>% select(ORDER,DATASET,TISSUE,STUDY_INSTITUTE,TECHNOLOGY,METAB_FAMILY,NAMED) %>%
  pivot_longer(cols = c('TISSUE','DATASET','STUDY_INSTITUTE','TECHNOLOGY','METAB_FAMILY','NAMED'),
               names_to = 'NAME', values_to = 'VALUE') %>% 
  mutate(NAME = factor(NAME, levels = c('TISSUE','DATASET','STUDY_INSTITUTE','TECHNOLOGY','METAB_FAMILY','NAMED') %>%
                         rev())) %>%
  arrange(ORDER)

# Generate distinct colors
qual_col_pals = brewer.pal.info[brewer.pal.info$category == 'qual',]
col_vector = unlist(mapply(brewer.pal, qual_col_pals$maxcolors, rownames(qual_col_pals)))
# Determine how many colors are neccessary
n <- length(unique(plot_df$VALUE))
# pie(rep(1,n), col=sample(col_vector, n)) # Pie chart of colors chosen

plot_df %>%
  ggplot(aes(x = ORDER, y = NAME)) + 
  geom_tile(aes(fill = VALUE),colour = "white") +
  theme(axis.title.x = element_blank()) +
  theme(axis.title.y = element_blank()) +
  theme(axis.text.x = element_blank()) +
  theme(legend.position = "none") +
  geom_text(aes(label=VALUE), angle=90, colour="black", size = 2) +
  scale_fill_manual(values=sample(col_vector, n))

```

### Investigate Rank Scores of Plots Between Sites: Stratified by Tissue
``` {r Investigate Rank Scores of Plots Between Sites: Stratified by Tissue}
# Collect Variables
#########################
# Types of data
data_types <- c("sxs-normalized-rank-df","mxm-normalized-rank-df")

# Comparisons ranked by number of metabolites shared in at least 1 tissue
shared_runs <- df_shared_casrun %>% filter(RUN_N == 2) %>% select(RUNS) %>% unlist() %>% as.character() %>% unique()

# DEV
############
# data_type <- "sxs-normalized-rank-df"
# tissue <- "brown-adipose"
# shared_run <- shared_runs[1]
# save_tf <- T

# Iterate through plot type (across tissues)
for(shared_run in shared_runs[1]){
  print(shared_run)
  # Adjust name
  shared_run_out <- shared_run %>% 
    str_replace_all('_','-') %>% str_replace_all(' ','-') %>% str_replace_all(';','_') %>% tolower()

  # Collect tissues based on frequency
  if(grepl('mayo',shared_run_out)){
    tissues <- df_shared_casrun %>% filter(RUN_N == 2) %>%
    filter(RUNS == shared_run) %>% select(TISSUE) %>% unlist() %>% as.character() %>% sort()
    tissues <- tissues[tissues %in% c("gastrocnemius","heart","lung","liver","white-adipose")]
  }else{
    tissues <- df_shared_casrun %>% filter(RUN_N == 2) %>%
    filter(RUNS == shared_run) %>% select(TISSUE) %>% unlist() %>% as.character() %>% sort()
  }
  all_rank_df <- data.frame()
  for(data_type in data_types){
      print(data_type)
    # Add the data type
      if(data_type == "sxs-normalized-rank-df"){
        dt <- 'SXS'
      }else if(data_type == "mxm-normalized-rank-df"){
        dt <- 'MXM'
      }
      # Iterate through tissues
      #tissue <- tissues[1]
      for(tissue in tissues){
          print(tissue)
          # Load the object into memory
          data_dir <- paste0(WD,"/data/site_comparisons/",shared_run_out)
          r_file <- paste0(data_dir,"/20201104_pass1a-metabolomics-",tissue,"-",data_type,"_steep.rds")
          rank_df <- readRDS(r_file)
          rank_df$COR_MTX <- dt
          names(all_rank_df)
          names(rank_df)[1] <- 'N_or_P'
          all_rank_df <- rbind(all_rank_df, rank_df)
      } # Iteration over tissues
  } # Iteration over data types
} # Iteration over runs

# Collect the medians for each tissue
med_ranks_df <- all_rank_df %>%
  group_by(TISSUE) %>%
  mutate(MEDIAN = median(RANK)) %>%
  arrange(MEDIAN) %>%
  select(TISSUE, MEDIAN, COR_MTX) %>% 
  unique() %>% ungroup() %>%
  split(.$COR_MTX) %>%
  map(~rename(., !!sym(unique(.$COR_MTX)) := "MEDIAN")) %>%
  map(~select(., -COR_MTX)) %>%
  purrr::reduce(left_join, by = c("TISSUE"))

# Create an scatterplot to examine correlation
######################
med_ranks_df %>%
  ggplot(aes(x = MXM, y = SXS)) +
  geom_text_repel(aes(label = TISSUE)) +
  geom_jitter(height = 0, width = 0, alpha = 0.8, size = 2)

# Histograms should be identical
##############################
med_ranks_df %>%
  ggplot(aes(x = MXM)) +
  geom_histogram()
med_ranks_df %>%
  ggplot(aes(x = SXS)) +
  geom_histogram()

# Visualize the ranks
#all_rank_df
med_ranks_df

```

### Visualize High Dimension Plots Between Sites: Stratified by Tissue
###### Plots are saved in intermediate directories under identical names. Locate, rename, and combine them in intuitive manner.
``` {r Visualize the Major Dimensions of the Metabolomics Pass1a (6mo) Hypercube}
# Collect Variables
#########################
# Types of plots
plot_types <- c("boxplot-original","density-original","mxm-original",
                "sxs-original","pca-original-0","pca-original-1","pca-original-2",
                "boxplot-normalized","density-normalized","mxm-normalized",
                "sxs-normalized","sxs-normalized-es","sxs-normalized-se",
                "pca-normalized-0","pca-normalized-1","pca-normalized-2")
plot_types <-c("sxs-normalized-es","sxs-normalized-se","mxm-normalized")
# Types of data
data_types <- c("sxs-normalized-rank-df","mxm-normalized-rank-df")

# Comparisons ranked by number of metabolites shared in at least 1 tissue
shared_runs <- df_shared_casrun %>% filter(RUN_N == 2) %>% select(RUNS) %>% unlist() %>% as.character() %>% unique()

# DEV
############
# plot_type <- "sxs-normalized"
# tissue <- "brown-adipose"
# shared_run <- shared_runs[1]

# Iterate through plot type (across tissues)
for(shared_run in shared_runs[1]){
  print(shared_run)
  # Adjust name
  shared_run_out <- shared_run %>% 
    str_replace_all('_','-') %>% str_replace_all(' ','-') %>% str_replace_all(';','_') %>% tolower()
  if(save_tf){
    # Create the output directory
    out_dir <- paste0(WD,'/plots/site_comparisons/across_tissues/',shared_run_out)
    cmd <- paste0('mkdir -p ',out_dir)
    system(cmd)
  }
  
  # Collect tissues based on frequency
  if(grepl('mayo',shared_run_out)){
    tissues <- df_shared_casrun %>% filter(RUN_N == 2) %>%
    filter(RUNS == shared_run) %>% select(TISSUE) %>% unlist() %>% as.character() %>% sort()
    tissues <- tissues[tissues %in% c("gastrocnemius","heart","lung","liver","white-adipose")]
  }else{
    tissues <- df_shared_casrun %>% filter(RUN_N == 2) %>%
    filter(RUNS == shared_run) %>% select(TISSUE) %>% unlist() %>% as.character() %>% sort()
  }
  for(plot_type in plot_types){
      print(plot_type)
      # Iterate through tissues
      i <- 1
      plot_list <- list()
      #tissue <- tissues[1]
      for(tissue in tissues){
          print(tissue)
          # Load the object into memory
          data_dir <- paste0(WD,"/data/site_comparisons/",shared_run_out)
          p_file <- paste0(data_dir,"/20201104_pass1a-metabolomics-",tissue,"-",plot_type,"_steep.rds")
          if(plot_type %in% c('mxm-original', 'mxm-normalized','sxs-original', 'sxs-normalized',
                              'sxs-normalized-se','sxs-normalized-es')){
            phm <- readRDS(p_file)
            plot_list[[i]] <- phm$gtable
          }else{
            plot_list[[i]] <- readRDS(p_file)
          }
          i <- i + 1
          }
   # Save the plots in a grid
    if(length(plot_list) == 1){
      nr <- 1
      nc <- 1
      w <- 10
      h <- 10
    }else if(length(plot_list) == 2){
      nr <- 1
      nc <- 2
      w <- 20
      h <- 30
    }else if(length(plot_list) == 3){
      nr <- 1
      nc <- 3
      w <- 30
      h <- 10
    }else if(length(plot_list) %in% c(4,5,6)){
      nr <- 2
      nc <- 3
      w <- 30
      h <- 20
    }else if(length(plot_list) %in% c(7,8,9)){
      nr <- 3
      nc <- 3
      w <- 30
      h <- 30
    }
  plots_out <- marrangeGrob(plot_list, nrow=nr, ncol=nc, 
                          layout_matrix = matrix(1:length(plot_list), nr, nc, TRUE))
  if(T){
    ggsave(paste0(WD,'/plots/site_comparisons/across_tissues/',shared_run_out,'/20201104_pass1a-metabolomics-',plot_type,'_steep.pdf'), plots_out,  width=w, height=h)
  }
  }
}


```


### Visualize Tissues Across Runs
```{r Visualize Tissues Across Runs}
# Types of plots
plot_types <- c("mxm-normalized","sxs-normalized",
                "pca-normalized-0","pca-normalized-1","pca-normalized-2")

# Comparisons ranked by number of metabolites shared in at least 1 tissue
shared_runs <- df_shared_casrun %>% filter(RUN_N == 2) %>% 
  filter(!grepl('Mayo', RUNS)) %>% 
  select(RUNS) %>% unlist() %>% as.character() %>% unique()
shared_runs <- shared_runs[c(12,1,14,2,4,3,10,5,7)]

shared_runs_out <- shared_runs %>% 
    str_replace_all('_','-') %>% str_replace_all(' ','-') %>% str_replace_all(';','_') %>% tolower()
tissues <- df_shared_casrun %>% filter(RUN_N == 2) %>%
  #   filter(RUNS %in% shared_runs[1:21]) %>% #These runs have ample overlap between targeted samples
  # filter(!grepl('Mayo', RUNS)) %>%
  select(TISSUE) %>% unlist() %>% as.character() %>% sort() %>% unique()

# tissue <- 'brown-adipose'
# Iterate through tissues
for(tissue in c('white-adipose')){
  print(tissue)
  # Create the output directory
  out_dir <- paste0(WD,'/plots/site_comparisons/',tissue)
  cmd <- paste0('mkdir -p ',out_dir)
  system(cmd)
  for(plot_type in plot_types){
      print(plot_type)
      # Iterate through tissues
      i <- 1
      plot_list <- list()
      #shared_run_out <- shared_runs_out[1]
      for(shared_run_out in shared_runs_out){
          print(shared_run_out)
          # Load the object into memory
          data_dir <- paste0(WD,"/data/site_comparisons/",shared_run_out)
          p_file <- paste0(data_dir,"/20201104_pass1a-metabolomics-",tissue,"-",plot_type,"_steep.rds")
          if(file.exists(p_file)){
            if(plot_type %in% c('mxm-original', 'mxm-normalized','sxs-original', 'sxs-normalized')){
            phm <- readRDS(p_file)
            plot_list[[i]] <- phm$gtable
          }else{
            plot_list[[i]] <- readRDS(p_file)
          }
          i <- i + 1
          }
          
          }
   # Save the plots in a grid
    if(length(plot_list) == 1){
      nr <- 1
      nc <- 1
      w <- 10
      h <- 10
    }else if(length(plot_list) == 2){
      nr <- 1
      nc <- 2
      w <- 20
      h <- 30
    }else if(length(plot_list) == 3){
      nr <- 1
      nc <- 3
      w <- 30
      h <- 10
    }else if(length(plot_list) %in% c(4,5,6)){
      nr <- 2
      nc <- 3
      w <- 30
      h <- 20
    }else if(length(plot_list) %in% c(7,8,9)){
      nr <- 3
      nc <- 3
      w <- 30
      h <- 30
    }
  plots_out <- marrangeGrob(plot_list, nrow=nr, ncol=nc, 
                          layout_matrix = matrix(1:length(plot_list), nr, nc, TRUE))
  ggsave(paste0(WD,'/plots/site_comparisons/',tissue,'/20201104_pass1a-metabolomics-',plot_type,'_steep.pdf'), plots_out,  width=w, height=h)
  }
}




```