---
title: "20201029_pass1a-metabolomics-targeted-cross-tissue_steep"
author: "Steep"
date: "10/29/2020"
always_allow_html: true
output: 
  github_document:
    toc: true
    #code_folding: hide
    #highlight: zenburn
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(cache = FALSE)
```

## Goals of Analysis
-Visualize the Data Structure of Metabolomics Data

## Setup the Environment
```{r Setup the Environment, message=FALSE, results='hide', warning = FALSE}
################################################################################
##### Resources and Dependencies ###############################################
################################################################################

# Set the working directory
#############################################################################
COMP <- "MacBook" 
#COMP <- "GreatLakes"       
if(COMP == "MacBook"){
        # MacBook
        WD <- '/Volumes/Frishman_4TB/motrpac/20200915_metabolomics-pass1a'    
}else if(COMP == "GreatLakes"){
        # MichMed
        WD <- '/home/acsteep/motrpac/20200915_metabolomics-pass1a'
}

#setwd(WD)

# Load the dependencies
#source("https://bioconductor.org/biocLite.R")
#BiocManager::install("org.Rn.eg.db")
#install.packages("kableExtra")

# Load dependencies
pacs...man <- c("tidyverse", "data.table","rlang","RColorBrewer","MASS","sfsmisc",
                "pheatmap","caret","ggforce","RANN","kableExtra")
lapply(pacs...man, FUN = function(X) {
        do.call("library", list(X)) })

############################################################
##### Functions ############################################
############################################################

# Name functions
select <- dplyr::select
counts <- DESeq2::counts
map <- purrr::map
desc <- dplyr::desc
arrange <- dplyr::arrange
melt <- reshape2::melt

# Global options
options(dplyr.print_max = 100)
options(scipen=10000)

# Source the functions
source(paste0(WD,'/functions/not_in.R'))
source(paste0(WD,'/functions/rat_mouse_ortho.R'))
source(paste0(WD,'/functions/mouse2rat_ortho.R'))
source(paste0(WD,'/functions/lmp.R'))
source(paste0(WD,'/functions/cor_PC_1_6.R'))
source(paste0(WD,'/functions/elbow_finder.R'))
source(paste0(WD,'/functions/cor_outlier2.R'))
source(paste0(WD,'/functions/DissimilarityMatrixNominal.R'))
source(paste0(WD,'/functions/lm_eqn.R'))
source(paste0(WD,'/functions/reorder_cormat.R'))
source(paste0(WD,'/functions/save_pheatmap_pdf.R'))
source(paste0(WD,'/functions/modeav.R'))
source(paste0(WD,'/functions/count_na.R'))
source(paste0(WD,'/functions/se_mean.R'))
source(paste0(WD,'/functions/Mode.R'))
source(paste0(WD,'/functions/NumericSummaryStats.R'))
source(paste0(WD,'/functions/AutoScaleMatrix.R'))
source(paste0(WD,'/functions/ReverseAutoScaleMatrix.R'))
source(paste0(WD,'/functions/CenterMatrix.R'))
source(paste0(WD,'/functions/RangeScaleMatrix.R'))
source(paste0(WD,'/functions/ParetoScaleMatrix.R'))
source(paste0(WD,'/functions/VastScaleMatrix.R'))
source(paste0(WD,'/functions/LevelScaleMatrix.R'))
source(paste0(WD,'/functions/Log10Matrix.R'))
source(paste0(WD,'/functions/PowerMatrix.R'))

```


# Set Variables
```{r Set Variables}

################################################################################
####################### Set Variables ##########################################
################################################################################

# Dataset
###################################
dataset <- 'untargeted'

# Named
###################################
named <- 'named'

# Tissue
###################################
tissue <- 'liver'

# Metabolite family
###################################
metab_family <- 'hilicpos'

# Transformation Technique
###################################
# Original Data
Untransformed <- 'COUNT_DATA'

# Correlation
###################################
Corr <- 'Pearson'
Corr <- 'Spearman'


```

# Load the Metadata and Count Data
```{r Load MetaData}
# Load the Data
################################################################################
# Files
metadata_rds <- paste0(WD, '/data/20201010_pass1a-metabolomics-metadata-table_steep.rds')
# Load Data
metadata_df <- readRDS(file = metadata_rds)

metadata_df %>%
  head(n =2) %>% kbl() %>% kable_styling()

# Start the clock
ptm <- proc.time()
# Takes 21+ seconds (881.6 Mb) 1073+ seconds for (7.5Gb)
#countdata_rds <- paste0(WD, #'/data/20201010_pass1a-metabolomics-countdata-nested_steep.rds')

# Load a specific tissues count data
# Liver takes 230 seconds (4 min)
#countdata_rds <- paste0(WD, '/data/20201010_pass1a-metabolomics-countdata-nested-',tissue,'_steep.rds')

# Load a specific metabolite family count data
# ac takes 2 seconds
# hilicpos takes 453 seconds (on MB) or 260 seconds (on GL with 40 MB 2 cores)
# All data (original + autoscaled) takes 170 seconds on MB
countdata_rds <- paste0(WD, '/data/20201010_pass1a-metabolomics-countdata-nested-orig_steep.rds')

# Load the data
countdata_df <- readRDS(file = countdata_rds)

# Stop the clock
proc.time() - ptm


```

# Load & Incorporate the Phenotype Data
```{r Incorporate Phenotype Data}
# Load the phenotype data
pheno_obj <- paste0(WD,"/data/20201021_pass1a-06-pheno-viallabel_steep.rds")
pheno_df <- readRDS(pheno_obj)

# Set a vector for Exercise/Control Levels and Colors
ec_levels <- c('Exercise - IPE',
               'Exercise - 0.5 hr',
               'Exercise - 1 hr',
               'Exercise - 4 hr',
               'Exercise - 7 hr',
               'Exercise - 24 hr',
               'Exercise - 48 hr',
               'Control - IPE',
               'Control - 7 hr')
ec_colors <- c('gold',
               'darkgoldenrod1',
               'orange',
               'darkorange',
               'darkorange2',
               'darkorange3',
               'darkorange4',
               'steelblue1',
               'steelblue4')

pheno_df %>%
  head(n =2) %>% kbl() %>% kable_styling()

```


# Explore Metadata
```{r Explore Metadata}

# First cut is either by tissue or metabolite family/tech
metadata_df %>% 
  select(TISSUE,METAB_FAMILY) %>% table() %>% as.data.frame.matrix() %>%
  select("hilicpos","rppos","rpneg","lrppos","lrpneg","ionpneg","cer","ac",
         "oxylipneg","tca","amines","sphm","ka","aa","3hib","nuc","acoa","oa","baiba") %>%
  arrange(desc("hilicpos"),desc("rppos"),desc("rpneg"),desc("lrppos"),desc("lrpneg"),
          desc("ionpneg"),desc("cer"),desc("ac"),desc("oxylipneg"),desc("tca"),
          desc("amines"),desc("sphm"),desc("ka"),desc("aa"),desc("3hib"),desc("nuc"),
          desc("acoa"),desc("oa"),desc("baiba"))

metadata_df %>% 
  filter(NAMED == 'named') %>%
  filter(METAB_FAMILY == metab_family) %>%
        select(DATASET,TISSUE,METAB_FAMILY,NAMED,STUDY_INSTITUTE,
               CH_CHROMATOGRAPHY_TYPE,MS_TYPE,MS_ION_MODE,DATASET) %>% 
        unite("CHROM_MS_ION", CH_CHROMATOGRAPHY_TYPE:MS_TYPE:MS_ION_MODE, remove = T)



```


# Collect the Shared Metabolites and Samples
```{r Collect Shared Metabolites and Samples}

# There are 20 tissues
# Shared metabolites across all 20 tissues
all_tis_mets <- countdata_df %>%
  filter(METAB_FAMILY == metab_family) %>%
  filter(NAMED == named) %>%
  select(-COUNT_DATA, -'SAMPLE_DATA') %>%
  unnest(cols = 'METABOLITE_DATA') %>%
  filter(!is.na(refmet_name)) %>%
  group_by(refmet_name) %>%
  mutate(SHARED_METABOLITE_N = n()) %>%
  arrange(desc(SHARED_METABOLITE_N)) %>%
  ungroup() %>%
  filter(SHARED_METABOLITE_N == 20) %>%
  select(refmet_name) %>% unlist() %>% as.character() %>% unique()
  
all_tis_mets

# Create a metadata table elongated to labelid (just the major metadata variables) from the count data df
meta_labelid_df <- countdata_df %>%
  filter(METAB_FAMILY == metab_family) %>%
  filter(NAMED == named) %>%
  select(-COUNT_DATA, -'METABOLITE_DATA') %>%
  unnest(cols = 'SAMPLE_DATA') %>%
  mutate(viallabel = sample_id) %>%
  select(-raw_file, -sample_id) %>%
  select(TISSUE, sample_type, viallabel) %>%
  unique()

```

# Examine the Relationship between metadata variables: Try to infer batches 
```{r}
metadata_df %>%
filter(METAB_FAMILY == metab_family) %>%
  filter(NAMED == named) %>%
  select(DATASET,NAMED,TISSUE,METAB_FAMILY,STUDY_INSTITUTE,CH_CHROMATOGRAPHY_TYPE,MS_TYPE,MS_ION_MODE) %>%
  unite(CH_CHROMATOGRAPHY_TYPE,MS_TYPE,MS_ION_MODE, col = "TECHNOLOGY") %>%
  arrange(TISSUE,STUDY_INSTITUTE,TECHNOLOGY)
```

# Examine the Distribution of the Original Data
# WARNING: Subsets of samples have been taken for development purposes
# Ensure that QC samples are not used in scaling
```{r Boxplots and Density Plots to Measure Distribution, results='asis'}
# Examine the Distributions for original data and transformed data
for(TFORM in c('Untransformed','AutoScaled')){
  #Starting with matrix: convert to long format dataframe for plotting purposes
  # When transforming, ensure that QC samples are not present
  if(TFORM == 'Untransformed'){
    tissue_long_df <- countdata_df %>%
    ungroup() %>%
    filter(METAB_FAMILY == metab_family) %>%
    filter(NAMED == named) %>%
    select(TISSUE, COUNT_DATA) %>%
    unnest(COUNT_DATA) %>%
    filter(METABOLITE_NAME %in% all_tis_mets) %>%
    filter(!grepl('QC', viallabel) ) %>%
    select(TISSUE,viallabel, METABOLITE_NAME,VALUE)
    
  }else if(TFORM == 'AutoScaled'){
    tissue_long_int <- countdata_df %>%
    ungroup() %>%
    filter(METAB_FAMILY == metab_family) %>%
    filter(NAMED == named) %>%
    select(TISSUE, COUNT_DATA) %>%
    unnest(COUNT_DATA) %>%
    filter(METABOLITE_NAME %in% all_tis_mets) %>%
    filter(!grepl('QC', viallabel) ) %>%
    select(viallabel, METABOLITE_NAME,VALUE) %>%
    pivot_wider(names_from = METABOLITE_NAME, values_from = VALUE) %>%
    tibble::column_to_rownames(var = "viallabel") %>%
    as.matrix() %>% 
    AutoScaleMatrix() %>%
    as.data.frame() %>%
    tibble::rownames_to_column(var = "viallabel") %>%
    pivot_longer(names_to = "METABOLITE_NAME", values_to = "VALUE", cols = all_of(all_tis_mets))
    
    # Join the tissues
    tissue_join <- countdata_df %>%
      ungroup() %>%
      filter(METAB_FAMILY == metab_family) %>%
      filter(NAMED == named) %>%
      select(TISSUE, COUNT_DATA) %>%
      unnest(COUNT_DATA) %>%
      filter(METABOLITE_NAME %in% all_tis_mets) %>%
      filter(!grepl('QC', viallabel) ) %>%
      select(viallabel,TISSUE) %>%
      unique()
    tissue_long_df <- left_join(tissue_long_int, tissue_join, by = c('viallabel'))
  }
  # Plot Boxplots for all shared metabolites faceted by tissue
  ################################################################################
  tissue_long_df$TISSUE <- factor(tissue_long_df$TISSUE)
  p <- tissue_long_df %>%
    slice_sample(prop = 0.1) %>%
    ggplot(aes(y = METABOLITE_NAME, x = VALUE)) +
    geom_boxplot(aes(color = TISSUE), alpha = 0.5) +
    labs(title="Box Plots of Metabolite Abundances Across Tissues",
               x = "Abundance", y = "") +
    theme(axis.text.y=element_text(size=4)) +
    theme(axis.text.x=element_text(size=8)) +
    theme(legend.text = element_text(size=8)) +
    facet_wrap(~ TISSUE)
  print(p)
# Plot the density plot for all the gene counts
################################################################################
  if(TFORM == 'Untransformed'){
    p <- tissue_long_df %>%
      slice_sample(prop = 0.1) %>%
      ggplot(aes(x = VALUE, color = TISSUE)) +
      geom_density() +
      labs(title="Density Plot of Metabolite Abundances Across Tissues",
           x = "Abundance",y = "Density") +
      facet_wrap(~ TISSUE) +
      xlim(0,1000000)
    }else if(TFORM == 'AutoScaled'){
      p <- tissue_long_df %>%
        slice_sample(prop = 0.1) %>%
        ggplot(aes(x = VALUE, color = TISSUE)) +
        geom_density() +
        labs(title="Density Plot of Metabolite Abundances Across Tissues",
             x = "Abundance",y = "Density") +
        facet_wrap(~ TISSUE)
      }
    print(p)

    # Summary Statistics of Density Plot Distribution Across Tissues
    ################################################################################
    tissues <- tissue_long_df$TISSUE %>% as.character() %>% unique()
    # Iterate through the cas sites and collect vectors
    #cas_site <- 'duke'
    df_all <- data.frame()
    #tt <- tissues[1]
    for(tt in tissues){
      # Collect numeric vector
      num_vec <- tissue_long_df %>%
        filter(TISSUE == tt) %>%
        select(VALUE) %>% unlist() %>% unname()
      df <- NumericSummaryStats(num_vec)
      row.names(df) <- tt
      df_all <- rbind(df_all, df)
    }
    df_all %>%
      arrange(MEDIAN) %>% print()
}

```

# Impute Missing Values (Necessary for PCA)
# Combine AutoScaled Datasets for PCA (Matrix; Columns:Metabolites, Rows: Unique_ID) (labelid+INSTITUTE+TECH))
-PREFA and PREFB are pooled samples for QC purposes
# PCA Analysis (Shared Samples and Shared Metabolites)
```{r Impute Missing Values + PCA}

for(TFORM in c('Untransformed','AutoScaled')){
  if(TFORM == 'Untransformed'){
    tissue_mat <- countdata_df %>%
    ungroup() %>%
    filter(METAB_FAMILY == metab_family) %>%
    filter(NAMED == named) %>%
    select(TISSUE, COUNT_DATA) %>%
    unnest(COUNT_DATA) %>%
    filter(METABOLITE_NAME %in% all_tis_mets) %>%
    mutate(viallabel = ifelse(grepl('QC_',viallabel), paste0(viallabel,'__',TISSUE), viallabel)) %>%
    select(viallabel, METABOLITE_NAME,VALUE) %>%
    pivot_wider(names_from = METABOLITE_NAME, values_from = VALUE) %>%
    tibble::column_to_rownames(var = "viallabel") %>%
    as.matrix()
  }else if(TFORM == 'AutoScaled'){
    tissue_mat <- countdata_df %>%
    ungroup() %>%
    filter(METAB_FAMILY == metab_family) %>%
    filter(NAMED == named) %>%
    select(TISSUE, COUNT_DATA) %>%
    unnest(COUNT_DATA) %>%
    filter(METABOLITE_NAME %in% all_tis_mets) %>%
    mutate(viallabel = ifelse(grepl('QC_',viallabel), paste0(viallabel,'__',TISSUE), viallabel)) %>%
    select(viallabel, METABOLITE_NAME,VALUE) %>%
    pivot_wider(names_from = METABOLITE_NAME, values_from = VALUE) %>%
    tibble::column_to_rownames(var = "viallabel") %>%
    as.matrix() %>% AutoScaleMatrix()
  }
  
  # Determine the proportion of missing data
  na_df <- data.frame()
  for(i in 1:ncol(tissue_mat)){
    # Collect numeric vector
    num_vec <- tissue_mat[,i] %>% unname()
    df <- NumericSummaryStats(num_vec)
    row.names(df) <- colnames(tissue_mat)[i]
    na_df <- rbind(na_df, df)
  }
  na_df %>% select(NA_COUNT, NA_FREQ) %>%
    filter(NA_FREQ > 0) %>%
    arrange(desc(NA_FREQ)) %>% kbl() %>% kable_styling()

  # Collect the major columns to be adjsuted
  imputed_cols10 <- na_df %>% select(NA_COUNT, NA_FREQ) %>%
    filter(NA_FREQ > 0) %>%
    arrange(desc(NA_FREQ)) %>%
    head(n = 10) %>% row.names()

  # Use a knn method to impute missing values (need to come back and adjust)
  preProcValues <- preProcess(tissue_mat,
                              method = c("knnImpute"),
                            k = floor(sqrt(ncol(tissue_mat))),
                            knnSummary = mean)
  # To get the normalizaed data
  impute_tissue_mat <- predict(preProcValues, tissue_mat, na.action = na.pass)
  # To denormalize ("deautoscale")
  tissue_mat_knn <- ReverseAutoScaleMatrix(impute_tissue_mat)

  # Examine the post impute data
  #summary(tissue_mat)
  #summary(tissue_mat_knn)

  # Plot a PCA with outliers labeled
  #dim(tissue_mat_knn)
  #tissue_mat_sam <- tissue_mat_knn[sample(1:nrow(tissue_mat_knn), 200),]

  pca <- prcomp(tissue_mat_knn, scale. = F)
  percentVar <- pca$sdev^2/sum(pca$sdev^2)
  PC <- pca$x %>% as.data.frame()
  PC$viallabel_tissue <- as.character(row.names(pca$x))
  PC <- PC %>%
    tidyr::separate(col = viallabel_tissue, into = c('viallabel', 'QCtissue'),
    sep = "__", remove = T)
  # Join the phenotype data and additional metadata
  PC <- left_join(PC, pheno_df, by = 'viallabel')
  meta_labelid_df1 <- meta_labelid_df %>%
    filter(sample_type == 'Sample') %>%
    mutate(sample_type = as.character(sample_type))
  meta_labelid_df2 <- meta_labelid_df %>%
    filter(sample_type != 'Sample')
  PC <- left_join(PC, meta_labelid_df1, by = 'viallabel') %>%
    mutate(sample_type = ifelse(grepl('QC_PREFA',viallabel), 'QC-DriftCorrection', sample_type)) %>%
    mutate(sample_type = ifelse(grepl('QC_PREFB',viallabel), 'QC-Pooled', sample_type)) %>%
    mutate(sample_type = ifelse(grepl('QC_Sed',viallabel), 'QC-Reference', sample_type)) %>%
    mutate(TISSUE = ifelse(grepl('QC_PREFA',viallabel), QCtissue, TISSUE)) %>%
    mutate(TISSUE = ifelse(grepl('QC_PREFB',viallabel), QCtissue, TISSUE)) %>%
    mutate(TISSUE = ifelse(grepl('QC_Sed',viallabel), QCtissue, TISSUE))
  table(PC$sample_type) %>% kbl() %>% kable_styling()

  PC %>%
    filter(sample_type %in% c('Sample','QC-Pooled')) %>%
    group_by(sample_type,TISSUE) %>%
      mutate(SAMPLE_N = n()) %>%
      select(sample_type,TISSUE,SAMPLE_N) %>%
      unique() %>% pivot_wider(names_from = sample_type, values_from = SAMPLE_N)

  # Clean up annotations
  PC$sample_type <- as.character(PC$sample_type)
  PC$TISSUE <- as.character(PC$TISSUE)
  PC_DRIFT <- PC %>%
    filter(sample_type %in% c('QC-DriftCorrection','Sample')) %>%
    mutate(QC_DRIFT = ifelse(sample_type == 'QC-DriftCorrection', 'QC-DriftCorrection' ,sample_type))
  PC_Pooled <- PC %>%
    filter(sample_type %in% c('QC-Pooled','Sample')) %>%
    mutate(QC_DRIFT = ifelse(sample_type == 'QC-Pooled', 'QC-Pooled' ,sample_type))
  PC_REF <- PC %>%
    filter(sample_type %in% c('QC-Reference','Sample')) %>%
    mutate(QC_DRIFT = ifelse(sample_type == 'QC-Reference', 'QC-Reference' ,sample_type))

  # Plot the pca (one outlier removed)
  p<- PC_Pooled %>%
    filter(viallabel != '90038016903') %>%
    mutate(dot_size = ifelse(grepl('QC',sample_type), 1.5, 1)) %>%
        ggplot(aes(x = PC1, y = PC2, color=TISSUE, shape = sample_type, size = dot_size)) +
        geom_point(alpha = 0.5) +
        ggtitle(paste0(metab_family,',',named,',',dataset,',','QC_Pooled',',',TFORM)) + 
        xlab(paste0('PC1: ',round(percentVar[1]*100,2),'% variance')) +
        ylab(paste0('PC2: ',round(percentVar[2]*100,2),'% variance'))
        #theme(aspect.ratio=1)
  print(p)
  p<- PC_REF %>%
    filter(viallabel != '90038016903') %>%
    mutate(dot_size = ifelse(grepl('QC',sample_type), 1.5, 1)) %>%
        ggplot(aes(x = PC1, y = PC2, color=TISSUE, shape = sample_type, size = dot_size)) +
        geom_point(alpha = 0.5) +
        ggtitle(paste0(metab_family,',',named,',',dataset,',','QC_REF',',',TFORM)) + 
        xlab(paste0('PC1: ',round(percentVar[1]*100,2),'% variance')) +
        ylab(paste0('PC2: ',round(percentVar[2]*100,2),'% variance'))
        #theme(aspect.ratio=1)
  print(p)
 
}


```






