---
title: "PASS1A (Rat) Metabolomics: Data Cleanup"
author: "Steep"
date: "10/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(cache = FALSE)
```

## Goals of Analysis
-Investigate the (what may be) biological replicates from Mayo

## Mayo-specific Annotations
-All targeted
-No normalization
-No drift correction
-No imputation
-Samples were divided into batches of ~20 for analysis

## Setup the Environment
```{r Setup the Environment, message=FALSE, results='hide', warning = FALSE, echo = FALSE}
################################################################################
##### Resources and Dependencies ###############################################
################################################################################

# Set the working directory
#############################################################################
COMP <- "MacBook" 
#COMP <- "GreatLakes"       
if(COMP == "MacBook"){
        # MacBook
        WD <- '/Volumes/Frishman_4TB/motrpac/20200915_metabolomics-pass1a'    
}else if(COMP == "GreatLakes"){
        # MichMed
        WD <- '/home/acsteep/motrpac/20200915_metabolomics-pass1a'
}

#setwd(WD)

# Load the dependencies
#source("https://bioconductor.org/biocLite.R")
#BiocManager::install("org.Rn.eg.db")
#install.packages("kableExtra")

# Load dependencies
pacs...man <- c("tidyverse", "data.table","rlang","RColorBrewer","MASS","sfsmisc",
                "pheatmap","caret","ggforce","RANN","kableExtra","gtools","combinat")
lapply(pacs...man, FUN = function(X) {
        do.call("library", list(X)) })

############################################################
##### Functions ############################################
############################################################

# Name functions
select <- dplyr::select
counts <- DESeq2::counts
map <- purrr::map
desc <- dplyr::desc
arrange <- dplyr::arrange
melt <- reshape2::melt
mutate <- dplyr::mutate

# Global options
options(dplyr.print_max = 100)
options(scipen=10000)

# Source the functions
source(paste0(WD,'/functions/not_in.R'))
source(paste0(WD,'/functions/rat_mouse_ortho.R'))
source(paste0(WD,'/functions/mouse2rat_ortho.R'))
source(paste0(WD,'/functions/lmp.R'))
source(paste0(WD,'/functions/cor_PC_1_6.R'))
source(paste0(WD,'/functions/elbow_finder.R'))
source(paste0(WD,'/functions/cor_outlier2.R'))
source(paste0(WD,'/functions/DissimilarityMatrixNominal.R'))
source(paste0(WD,'/functions/lm_eqn.R'))
source(paste0(WD,'/functions/reorder_cormat.R'))
source(paste0(WD,'/functions/save_pheatmap_pdf.R'))
source(paste0(WD,'/functions/modeav.R'))
source(paste0(WD,'/functions/count_na.R'))
source(paste0(WD,'/functions/se_mean.R'))
source(paste0(WD,'/functions/Mode.R'))
source(paste0(WD,'/functions/NumericSummaryStats.R'))
source(paste0(WD,'/functions/AutoScaleMatrix.R'))
source(paste0(WD,'/functions/ReverseAutoScaleMatrix.R'))
source(paste0(WD,'/functions/CenterMatrix.R'))
source(paste0(WD,'/functions/RangeScaleMatrix.R'))
source(paste0(WD,'/functions/ParetoScaleMatrix.R'))
source(paste0(WD,'/functions/VastScaleMatrix.R'))
source(paste0(WD,'/functions/LevelScaleMatrix.R'))
source(paste0(WD,'/functions/Log10Matrix.R'))
source(paste0(WD,'/functions/PowerMatrix.R'))

```


# Set Variables
```{r Set Variables}

################################################################################
####################### Set Variables ##########################################
################################################################################

# Should shared metabolites and samples be calculated?
###################################
COLLECT_SHARED <- FALSE

# Dataset
###################################
dataset <- 'targeted'

# Named
###################################
named <- 'named'

# Tissue
###################################
tissue <- 'liver'

# Metabolite family
###################################
metab_family <- 'amines'

# Correlation
###################################
#Corr <- 'Pearson'
Corr <- 'Spearman'


```

# Load the Metadata and Count Data
```{r Load MetaData}
# Load the Data
################################################################################
# Files
metadata_rds <- paste0(WD, '/data/20201010_pass1a-metabolomics-metadata-table_steep.rds')
# Load Data
metadata_df <- readRDS(file = metadata_rds)

metadata_df %>%
  head(n =2) %>% kbl() %>% kable_styling()

# Start the clock
ptm <- proc.time()
# Takes 21+ seconds (881.6 Mb) 1073+ seconds for (7.5Gb)
#countdata_rds <- paste0(WD, #'/data/20201010_pass1a-metabolomics-countdata-nested_steep.rds')

# Load a specific tissues count data
# Liver takes 230 seconds (4 min)
#countdata_rds <- paste0(WD, '/data/20201010_pass1a-metabolomics-countdata-nested-',tissue,'_steep.rds')

# Load a specific metabolite family count data
# ac takes 2 seconds
# hilicpos takes 453 seconds (on MB) or 260 seconds (on GL with 40 MB 2 cores)
# All data (original + autoscaled) takes 170 seconds on MB
countdata_rds <- paste0(WD, '/data/20201010_pass1a-metabolomics-countdata-nested_steep.rds')

# Load the data
countdata_df <- readRDS(file = countdata_rds)

# Stop the clock
proc.time() - ptm
```

# Load & Incorporate the Phenotype Data
```{r Incorporate Phenotype Data}
# Load the phenotype data
pheno_obj <- paste0(WD,"/data/20201021_pass1a-06-pheno-viallabel_steep.rds")
pheno_df <- readRDS(pheno_obj)

# Set a vector for Exercise/Control Levels and Colors
ec_levels <- c('Exercise - IPE',
               'Exercise - 0.5 hr',
               'Exercise - 1 hr',
               'Exercise - 4 hr',
               'Exercise - 7 hr',
               'Exercise - 24 hr',
               'Exercise - 48 hr',
               'Control - IPE',
               'Control - 7 hr')
ec_colors <- c('gold',
               'darkgoldenrod1',
               'orange',
               'darkorange',
               'darkorange2',
               'darkorange3',
               'darkorange4',
               'steelblue1',
               'steelblue4')

pheno_df %>%
  head(n =2) %>% kbl() %>% kable_styling()
```

# Visualize the number of samples and number of metabolites across all "named" batches
```{r Explore Metadata}

# Order of Sites and metab_family
site_metab_order <- metadata_df %>%
  unite(STUDY_INSTITUTE, METAB_FAMILY, col = "SITE_METAB") %>%
  select(TISSUE,SITE_METAB,SAMPLE_N,QC_IS_N,QC_PRERUN_N,QC_BLANK_N,
          QC_POOLED_N,QC_REFERENCE_N,QC_DRIFT_N,METABOLITE_N) %>%
  group_by(SITE_METAB) %>%
  select(SITE_METAB,SAMPLE_N) %>%
  mutate(SAMPLE_SUM = sum(SAMPLE_N)) %>%
  select(SITE_METAB, SAMPLE_SUM) %>%
  arrange(desc(SAMPLE_SUM)) %>% unique() %>%
  select(SITE_METAB) %>% unlist() %>% as.character() %>% unique()

# Order of tissues
tissue_order <- metadata_df %>%
  unite(STUDY_INSTITUTE, METAB_FAMILY, col = "SITE_METAB") %>%
  select(TISSUE,SITE_METAB,SAMPLE_N,QC_IS_N,QC_PRERUN_N,QC_BLANK_N,
          QC_POOLED_N,QC_REFERENCE_N,QC_DRIFT_N,METABOLITE_N) %>%
  group_by(TISSUE) %>%
  mutate(SAMPLE_SUM = sum(SAMPLE_N)) %>%
  select(TISSUE, SAMPLE_SUM) %>%
  arrange(desc(SAMPLE_SUM)) %>% unique() %>%
  select(TISSUE) %>% unlist() %>% as.character() %>% unique() %>% rev()
  
# Create a plot of sample number by tissue and technology
metadata_df %>%
  unite(STUDY_INSTITUTE, METAB_FAMILY, col = "SITE_METAB") %>%
  select(TISSUE,SITE_METAB,SAMPLE_N,QC_IS_N,QC_PRERUN_N,QC_BLANK_N,
          QC_POOLED_N,QC_REFERENCE_N,QC_DRIFT_N,METABOLITE_N) %>%
  mutate(TISSUE = factor(TISSUE, levels = tissue_order)) %>%
  mutate(SITE_METAB = factor(SITE_METAB, levels = site_metab_order)) %>%
  ggplot(aes(SITE_METAB,TISSUE)) +
    geom_tile(aes(fill = SAMPLE_N)) + 
    geom_text(aes(label = SAMPLE_N)) +
    scale_fill_gradient(low = "white", high = "red") +
  ggtitle("Samples Across Named Runs") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.title.x = element_blank(),
  axis.title.y = element_blank()) +
  theme(legend.position = "none") +
  scale_x_discrete(position = "top") +
  theme(axis.text.x = element_text(angle = 300, hjust = 0.9))

# METABOLITE_NAMED_N
# Create a plot of sample number by tissue and technology
metadata_df %>%
  unite(STUDY_INSTITUTE, METAB_FAMILY, col = "SITE_METAB") %>%
  select(TISSUE,NAMED,SITE_METAB,SAMPLE_N,QC_IS_N,QC_PRERUN_N,QC_BLANK_N,
          QC_POOLED_N,QC_REFERENCE_N,QC_DRIFT_N,METABOLITE_N) %>%
  mutate(TISSUE = factor(TISSUE, levels = tissue_order)) %>%
  mutate(SITE_METAB = factor(SITE_METAB, levels = site_metab_order)) %>%
  filter(NAMED == 'named') %>%
  mutate(METABOLITE_NAMED_N = 0) %>%
  mutate(METABOLITE_NAMED_N = ifelse(NAMED == 'named', METABOLITE_N, METABOLITE_NAMED_N)) %>%
  ggplot(aes(SITE_METAB,TISSUE)) +
    geom_tile(aes(fill = METABOLITE_NAMED_N)) + 
    geom_text(aes(label = METABOLITE_NAMED_N)) +
    scale_fill_gradient(low = "white", high = "red") +
  ggtitle("Named Metabolites Across Runs") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.title.x = element_blank(),
  axis.title.y = element_blank()) +
  theme(legend.position = "none") +
  scale_x_discrete(position = "top") +
  theme(axis.text.x = element_text(angle = 300, hjust = 0.9))

```

# Explore the metadata to investigate this statement:
-"Samples were divided into batches of ~20 for analysis"

```{r Batches of 20}
# Assign Variables
################################################################################
tissue_study_institute_metab_families <- countdata_df %>%
  ungroup() %>%
  filter(STUDY_INSTITUTE == 'Mayo Clinic') %>%
  unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
  unite(TISSUE,STUDY_INSTITUTE_METAB_FAMILY, col = TISSUE_STUDY_INSTITUTE_METAB_FAMILY) %>%
  select(TISSUE_STUDY_INSTITUTE_METAB_FAMILY) %>% unlist() %>% as.character() %>% unique()

# Are all samples divisible by 20?
metadata_df %>%
  unite(STUDY_INSTITUTE, METAB_FAMILY, col = "SITE_METAB") %>%
  filter(grepl("Mayo Clinic", SITE_METAB)) %>%
  select(TISSUE,SITE_METAB,SAMPLE_N,QC_IS_N,QC_PRERUN_N,QC_BLANK_N,
          QC_POOLED_N,QC_REFERENCE_N,QC_DRIFT_N) %>%
  mutate(ALL_SAMPLE_N = SAMPLE_N + QC_IS_N + QC_PRERUN_N + QC_BLANK_N + QC_POOLED_N +
                            QC_REFERENCE_N + QC_DRIFT_N) %>%
  mutate(ALL_SAMPLE_N_D20 = ALL_SAMPLE_N/20)
# x %>%
#   select(ALL_SAMPLE_N_D20) %>%
#   mutate(ALL_SAMPLE_N_D20 = ALL_SAMPLE_N_D20 %>% str_split(pattern = '\\.') %>% 
#            map(tail, 1) %>% unlist() %>% as.numeric()) %>%
#   mutate(ALL_SAMPLE_N_D20 = paste0('0.', as.character(ALL_SAMPLE_N_D20)) %>% as.numeric()) %>%
#   unlist() %>%
#   hist(breaks = 100) +
#   xlim(0,1)

# DEV
tissue_study_institute_metab_family <- "plasma_Mayo Clinic_ac"
for(tissue_study_institute_metab_family in tissue_study_institute_metab_families[1]){
  # Variables
  tissue <- tissue_study_institute_metab_family %>% 
    str_split(pattern = '_') %>% unlist() %>% head(n=1)
  study_institute_metab_family <- tissue_study_institute_metab_family %>%
    str_remove(paste0(tissue,'_'))
  named <- 'named'
  
  # Collect the samples (keep QCs) & join sample order
  sample_join <- countdata_df %>%
        ungroup() %>%
        unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
        filter(TISSUE == tissue) %>%
        filter(NAMED == named) %>%
        filter(STUDY_INSTITUTE_METAB_FAMILY == study_institute_metab_family) %>%
        unnest(SAMPLE_DATA) %>%
    select(sample_id, sample_type, sample_order, raw_file)
  
  # Subset Data
################################################################################
  # Collect the samples (remove QCs) & join sample order
p <- countdata_df %>%
    ungroup() %>%
    unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
    filter(TISSUE == tissue) %>%
    filter(NAMED == named) %>%
    filter(STUDY_INSTITUTE_METAB_FAMILY == study_institute_metab_family) %>%
    unnest(COUNT_DATA) %>%
    select(-SAMPLE_DATA) %>%
    left_join(y = sample_join, by = c("viallabel" = "sample_id")) %>%
    select(STUDY_INSTITUTE_METAB_FAMILY,labelid, viallabel, pid, bid,sample_type,sample_order,raw_file) %>%
    unique() %>%
    mutate(alt_sample_order = raw_file %>% str_split(pattern = '_') %>% map(tail, 1) %>% unlist()) %>%
    arrange(raw_file, alt_sample_order)
  print(p)
}

```
# Questions for Mayo:
-What was the role of QC_POOLED and QC_REFERENCE samples?
-How were QC samples divided across runs?
-"raw_file" seems to represent a date and an additiona number (date_#)
  -What is the significance of this number? Does it represent a sample order
-How was "sample_order" determined?
-How were batches divided across samples and QCs?

# Some runs from Mayo have duplicate abundance measurements
Metabolite families:
-ac, amines, cer, tca
Within Tissues:
-liver, gastrocnemius, white-adipose, lung, heart, brown-adipose, kidney

# Determine if sites contain replicates
# Ensure that the Replicates contain the same labelids
```{r}
# Assign Variables
################################################################################
tissue_study_institute_metab_families <- countdata_df %>%
  ungroup() %>%
  unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
  unite(TISSUE,STUDY_INSTITUTE_METAB_FAMILY, col = TISSUE_STUDY_INSTITUTE_METAB_FAMILY) %>%
  select(TISSUE_STUDY_INSTITUTE_METAB_FAMILY) %>% unlist() %>% as.character() %>% unique()

# DEV
# study_institute_metab_family <- "Mayo Clinic_ac"
# tissue <- 'brown-adipose'
# tissue_study_institute_metab_familiy <- tissue_study_institute_metab_families[1]
for(tissue_study_institute_metab_family in tissue_study_institute_metab_families){
  # Variables
  tissue <- tissue_study_institute_metab_family %>% 
    str_split(pattern = '_') %>% unlist() %>% head(n=1)
  study_institute_metab_family <- tissue_study_institute_metab_family %>%
    str_remove(paste0(tissue,'_'))
  named <- 'named'
  
  # Subset Data
################################################################################
  # Collect the samples (remove QCs) & join sample order
sample_join <- countdata_df %>%
        ungroup() %>%
        unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
        filter(TISSUE == tissue) %>%
        filter(NAMED == named) %>%
        filter(STUDY_INSTITUTE_METAB_FAMILY == study_institute_metab_family) %>%
        unnest(SAMPLE_DATA) %>%
        filter(sample_type == 'Sample') %>%
        select(sample_id, sample_order)
  
  # Determine the number of replicates based on viallabel ending
  reps <- countdata_df %>%
  ungroup() %>%
  unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
  filter(TISSUE == tissue) %>%
  filter(NAMED == named) %>%
  filter(STUDY_INSTITUTE_METAB_FAMILY == study_institute_metab_family) %>%
  unnest(COUNT_DATA) %>%
  filter(viallabel %in% as.character(unlist(sample_join$sample_id))) %>%
    select(viallabel) %>% unlist() %>% as.character() %>% unique() %>%
    str_sub(-3,-1) %>% unique()
  
  if(length(reps) >= 2){
    # Print the number of replicates
    print(paste0('Number of replicates in ',tissue,' ',study_institute_metab_family,': ', length(reps)))
    print(paste0('Replicates in ',tissue,' ',study_institute_metab_family,': ', paste(reps, collapse = ' ')))
  
    rep_df <- countdata_df %>%
    ungroup() %>%
    unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
    filter(TISSUE == tissue) %>%
    filter(NAMED == named) %>%
    filter(STUDY_INSTITUTE_METAB_FAMILY == study_institute_metab_family) %>%
    unnest(COUNT_DATA) %>%
    filter(viallabel %in% as.character(unlist(sample_join$sample_id))) %>%
    #left_join(y = sample_join, by = c("viallabel" = "sample_id")) %>%
    unite(labelid, viallabel, col = "labelid_viallabel", remove = F) %>%
    mutate(REPLICATE = case_when(grepl(paste0(reps[1],"$"),labelid_viallabel) ~ reps[1],
                               grepl(paste0(reps[2],"$"),labelid_viallabel) ~ reps[2])) %>%
    select(REPLICATE,labelid_viallabel, labelid, viallabel, pid, bid, METABOLITE_NAME,VALUE)
    
    # rep_summary <- rep_df %>%
    #   mutate(REPLICATE = factor(REPLICATE)) %>%
    #   mutate(labelid_viallabel = factor(labelid_viallabel)) %>%
    #   mutate(labelid = factor(labelid)) %>%
    #   mutate(viallabel = factor(viallabel)) %>%
    #   mutate(pid = factor(pid)) %>%
    #   mutate(bid = factor(bid)) %>%
    #   mutate(METABOLITE_NAME = factor(METABOLITE_NAME)) %>%
    #   select(-VALUE) %>% unique()
    # summary(rep_summary)
    # rep_df %>% select(labelid) %>% table()
    
    r1_v <- rep_df %>%
    filter(REPLICATE == reps[1]) %>%
    select(labelid) %>% unlist() %>% as.character() %>% sort()
    r2_v <- rep_df %>%
    filter(REPLICATE == reps[2]) %>%
    select(labelid) %>% unlist() %>% as.character() %>% sort()
    length(r1_v)
    length(r2_v)
    print(all(r1_v == r2_v))
  }
}
```



# Per Run, Split the Data by duplicates and plot boxplots and matched density plot before normalization
# Normalize and plot boxplots and matched density plot after normalization
-Boxplots
-Density plot
-Summary Statistics
```{r Boxplots and Density Plots to Measure Normalization}

# Assign Variables
################################################################################
tissue_study_institute_metab_families <- countdata_df %>%
  ungroup() %>%
  unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
  unite(TISSUE,STUDY_INSTITUTE_METAB_FAMILY, col = TISSUE_STUDY_INSTITUTE_METAB_FAMILY) %>%
  select(TISSUE_STUDY_INSTITUTE_METAB_FAMILY) %>% unlist() %>% as.character() %>% unique()

# DEV
# study_institute_metab_family <- "Mayo Clinic_ac"
# tissue <- 'liver'
# tissue_study_institute_metab_familiy <- tissue_study_institute_metab_families[1]
for(tissue_study_institute_metab_family in tissue_study_institute_metab_families){
  # Variables
  tissue <- tissue_study_institute_metab_family %>% 
    str_split(pattern = '_') %>% unlist() %>% head(n=1)
  study_institute_metab_family <- tissue_study_institute_metab_family %>%
    str_remove(paste0(tissue,'_'))
  named <- 'named'
  
  # Collect the samples (remove QCs) & join sample order
  sample_join <- countdata_df %>%
        ungroup() %>%
        unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
        filter(TISSUE == tissue) %>%
        filter(NAMED == named) %>%
        filter(STUDY_INSTITUTE_METAB_FAMILY == study_institute_metab_family) %>%
        unnest(SAMPLE_DATA) %>%
        filter(sample_type == 'Sample') %>%
        select(sample_id, sample_order)

  # Determine the number of replicates based on viallabel ending
  reps <- countdata_df %>%
  ungroup() %>%
  unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
  filter(TISSUE == tissue) %>%
  filter(NAMED == named) %>%
  filter(STUDY_INSTITUTE_METAB_FAMILY == study_institute_metab_family) %>%
  unnest(COUNT_DATA) %>%
  filter(viallabel %in% as.character(unlist(sample_join$sample_id))) %>%
    select(viallabel) %>% unlist() %>% as.character() %>% unique() %>%
    str_sub(-3,-1) %>% unique()
  # If the runs contain replicate samples, then proceed with the analysis
  if(length(reps) == 2){
    # Print the number of replicates
    print(paste0('Number of replicates in ',tissue,' ',study_institute_metab_family,': ', length(reps)))
    print(paste0('Replicates in ',tissue,' ',study_institute_metab_family,': ', paste(reps, collapse = ' ')))

    # Collect the metabolites unique to run
    metabolites <- countdata_df %>%
        ungroup() %>%
        unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
        filter(TISSUE == tissue) %>%
        filter(NAMED == named) %>%
        filter(STUDY_INSTITUTE_METAB_FAMILY == study_institute_metab_family) %>%
        unnest(METABOLITE_DATA) %>%
        select(refmet_name) %>% unlist() %>% as.character() %>% unique()

# Subset Data
################################################################################

# Collect abundances in long format and annotate replicate labelids
plot_df <- countdata_df %>%
        ungroup() %>%
        unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
        filter(TISSUE == tissue) %>%
        filter(NAMED == named) %>%
        filter(STUDY_INSTITUTE_METAB_FAMILY == study_institute_metab_family) %>%
        unnest(COUNT_DATA) %>%
        filter(viallabel %in% as.character(unlist(sample_join$sample_id))) %>%
        left_join(y = sample_join, by = c("viallabel" = "sample_id")) %>%
        unite(labelid, viallabel, col = "labelid_viallabel", remove = F) %>%
        mutate(REPLICATE = case_when(grepl(paste0(reps[1],"$"),labelid_viallabel) ~ reps[1],
                                     grepl(paste0(reps[2],"$"),labelid_viallabel) ~ reps[2],
                                     grepl(paste0(reps[3],"$"),labelid_viallabel) ~ reps[3]))

# Plot Boxplots faceted by shared metabolites
################################################################################
p <- plot_df %>%
  ggplot(aes(y = METABOLITE_NAME, x = VALUE, color = REPLICATE)) +
  geom_boxplot(alpha = 0.8) +
  labs(title=paste0(tissue,' ',study_institute_metab_family,": Original Metabolite Abundances"),
             x = "Abundance", y = "") 
plot(p)

# Summary Statistics of Density plot distribution
################################################################################
# Iterate through the runs and collect vectors
df_all <- data.frame()
for(rep in c(reps)){
  # Collect numeric vector
  num_vec <- plot_df %>%
    filter(REPLICATE == rep) %>%
    select(VALUE) %>% unlist() %>% unname()
  df <- NumericSummaryStats(num_vec)
  row.names(df) <- rep
  df_all <- rbind(df_all, df)
}
p <- df_all
print(p)

# Plot the density plot for all the gene counts
################################################################################
p <- plot_df %>%
  ggplot(aes(x = VALUE, color = REPLICATE)) +
  geom_density() +
  xlim(min(df_all$MIN), mean(df_all$Q3)) +
  labs(title=paste0(tissue,' ',study_institute_metab_family,": Original Metabolite Abundances"),
       x = "Abundance",
       y = "Density")
plot(p)

# Subset the data for sites to compare (scatterplots)
###################################################
plot_join_df <- countdata_df %>%
  ungroup() %>%
  unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
  filter(TISSUE == tissue) %>%
  filter(NAMED == named) %>%
  filter(STUDY_INSTITUTE_METAB_FAMILY == study_institute_metab_family) %>%
  unnest(COUNT_DATA) %>%
  filter(viallabel %in% as.character(unlist(sample_join$sample_id))) %>%
  unite(labelid, viallabel, col = "labelid_viallabel", remove = F) %>%
  mutate(REPLICATE = case_when(grepl(paste0(reps[1],"$"),labelid_viallabel) ~ reps[1],
                              grepl(paste0(reps[2],"$"),labelid_viallabel) ~ reps[2],
                              )) %>%
  select(REPLICATE,METABOLITE_NAME,labelid,VALUE) %>%
  mutate(REPLICATE = as.character(REPLICATE)) %>%
  split(.$REPLICATE) %>%
  map(~rename(., !!sym(unique(.$REPLICATE)) := "VALUE")) %>%
  map(~select(., -REPLICATE)) %>%
  purrr::reduce(left_join, by = c("labelid","METABOLITE_NAME"))

# Normalize
# Note in this step, we use labelid to account for mayo's duplicate samples
################################################################################
norm_df <- plot_df %>%
  unite(labelid, viallabel, col = "labelid_viallabel", remove = F) %>%
  split(.$REPLICATE) %>%
  map(select, labelid_viallabel, METABOLITE_NAME, VALUE) %>%
  map(pivot_wider, names_from = METABOLITE_NAME, values_from = VALUE) %>%
  map(column_to_rownames, var = "labelid_viallabel") %>%
  map(as.matrix) %>%
  map(AutoScaleMatrix) %>%
  map(as.data.frame) %>%
  map(rownames_to_column, var = "labelid_viallabel") %>%
  map(pivot_longer, names_to = 'METABOLITE_NAME', values_to = 'VALUE', cols = all_of(metabolites)) %>%
  map(mutate, REPLICATE = case_when(grepl(paste0(reps[1],"$"),labelid_viallabel) ~ reps[1],
                                     grepl(paste0(reps[2],"$"),labelid_viallabel) ~ reps[2],
                                    grepl(paste0(reps[3],"$"),labelid_viallabel) ~ reps[3])) %>%
  bind_rows()

# Plot Boxplots faceted by shared metabolites
################################################################################
p <- norm_df %>%
  ggplot(aes(y = METABOLITE_NAME, x = VALUE, color = REPLICATE)) +
  geom_boxplot(alpha = 0.8) +
  labs(title=paste0(tissue,' ',study_institute_metab_family,": Normalized Metabolite Abundances"),
             x = "Abundance", y = "") 
print(p)
# Normalize
# Subset the data for sites to compare (scatterplots)
###################################################
norm_join_df <- countdata_df %>%
  ungroup() %>%
  unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
  filter(TISSUE == tissue) %>%
  filter(NAMED == named) %>%
  filter(STUDY_INSTITUTE_METAB_FAMILY == study_institute_metab_family) %>%
  unnest(COUNT_DATA) %>%
  filter(viallabel %in% as.character(unlist(sample_join$sample_id))) %>%
  unite(labelid, viallabel, col = "labelid_viallabel", remove = F) %>%
  mutate(REPLICATE = case_when(grepl(paste0(reps[1],"$"),labelid_viallabel) ~ reps[1],
                                     grepl(paste0(reps[2],"$"),labelid_viallabel) ~ reps[2],
                               grepl(paste0(reps[3],"$"),labelid_viallabel) ~ reps[3])) %>%
  split(.$REPLICATE) %>%
  map(select, labelid_viallabel, METABOLITE_NAME, VALUE) %>%
  map(pivot_wider, names_from = METABOLITE_NAME, values_from = VALUE) %>%
  map(column_to_rownames, var = "labelid_viallabel") %>%
  map(as.matrix) %>%
  map(AutoScaleMatrix) %>%
  map(as.data.frame) %>%
  map(rownames_to_column, var = "labelid_viallabel") %>%
  map(pivot_longer, names_to = 'METABOLITE_NAME', values_to = 'VALUE', cols = all_of(metabolites)) %>%
  map(mutate, REPLICATE = case_when(grepl(paste0(reps[1],"$"),labelid_viallabel) ~ reps[1],
                                     grepl(paste0(reps[2],"$"),labelid_viallabel) ~ reps[2],
                                    grepl(paste0(reps[3],"$"),labelid_viallabel) ~ reps[3])) %>%
  map(~rename(., !!sym(unique(.$REPLICATE)) := "VALUE")) %>%
  map(~select(., -REPLICATE)) %>%
  map(mutate, labelid = gsub(pattern = "_..*", replacement = '', labelid_viallabel)) %>%
  map(select, -labelid_viallabel) %>%
  purrr::reduce(left_join, by = c("labelid","METABOLITE_NAME"))

# Plot scatter plots
################################################################################
p <- norm_join_df %>%
  ggplot(aes(x = !!sym(reps[1]), y = !!sym(reps[2])), color = ) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", size = 1) +
  geom_abline(linetype="dashed") +
  facet_wrap(~ METABOLITE_NAME) +
  expand_limits(x = 0, y = 0) +
  labs(title=paste0(tissue,' ',study_institute_metab_family,": Normalized Metabolite Abundances")) +
  coord_fixed(ratio=1)
plot(p)

# Plot scatter plots ordered by sample (include R2 values)
lm_df <- norm_join_df %>%
  rename(name = METABOLITE_NAME) %>%
  rename(x = reps[1]) %>%
  rename(y = reps[2])
# Iterate through each of the shared metabolites to collect summary info about their correlations
r2_df <- data.frame()
for(metab in metabolites){
  met_df <- lm_df %>%
    filter(name == metab)
  r2_df <- rbind(r2_df, lm_eqn(met_df))
}



# Display summaries
p <- r2_df %>%
  arrange(METABOLITE)
print(p)
p <- r2_df %>%
  arrange(desc(R2)) %>%
  select(METABOLITE,R2)
print(p)

# Plot the density plot for all the gene counts
################################################################################
p <- norm_df %>%
  ggplot(aes(x = VALUE, color = REPLICATE)) +
  geom_density() +
  labs(title=paste0(tissue,' ',study_institute_metab_family,": Normalized Metabolite Abundances"),
       x = "Abundance",
       y = "Density")
plot(p)
# Summary Statistics of Density plot distribution
################################################################################
# Iterate through the runs and collect vectors
df_all <- data.frame()
for(rep in reps){
  # Collect numeric vector
  num_vec <- norm_df %>%
    filter(REPLICATE == rep) %>%
    select(VALUE) %>% unlist() %>% unname()
  df <- NumericSummaryStats(num_vec)
  row.names(df) <- rep
  df_all <- rbind(df_all, df)
}
p <- df_all
print(p)
}

}

```

# Inference:
-It seems there are differences in metabolite meaures (measured by correlation and plotting) between the different replicates. We should consider why these samples were replicated.

# #### Sesh:
```{r Sesh}
session_info()
```



