---
title: | 
 | PASS1A (Rat) Metabolomics: 
 | Mayo Clinic Replicate Comparisons (Pairs)
author: "Alec Steep"
date: "10/12/2020"
#always_allow_html: true
output:
     html_document:
         code_folding: hide
         toc: true
         highlight: zenburn
         css: ../css/style.css
---

### Setup the Environment
```{r Setup the Environment, message=FALSE, results='hide', warning = FALSE, echo = FALSE}
################################################################################
##### Resources and Dependencies ###############################################
################################################################################

# Set the working directory
#############################################################################
COMP <- "MacBook" 
#COMP <- "GreatLakes"       
if(COMP == "MacBook"){
        # MacBook
        WD <- '/Volumes/Frishman_4TB/motrpac/20200915_metabolomics-pass1a'    
}else if(COMP == "GreatLakes"){
        # MichMed
        WD <- '/home/acsteep/motrpac/20200915_metabolomics-pass1a'
}

#setwd(WD)

# Load the dependencies
#source("https://bioconductor.org/biocLite.R")
#BiocManager::install("org.Rn.eg.db")
#install.packages("kableExtra")

# Load dependencies
pacs...man <- c("tidyverse", "data.table","rlang","RColorBrewer","MASS","sfsmisc",
                "pheatmap","caret","ggforce","RANN","kableExtra","gtools","combinat",
                "knitr","markdown","rmarkdown","gridExtra","cowplot")
for(pac in pacs...man){
  suppressWarnings(suppressPackageStartupMessages(library(pac, character.only = TRUE)))
}
# lapply(pacs...man, FUN = function(X) {
#         do.call("library", list(X)) })

############################################################
##### Functions ############################################
############################################################

# Name functions
select <- dplyr::select
counts <- DESeq2::counts
map <- purrr::map
desc <- dplyr::desc
arrange <- dplyr::arrange
melt <- reshape2::melt
mutate <- dplyr::mutate

# Global options
options(dplyr.print_max = 100)
options(scipen=10000)

# Source the functions
source(paste0(WD,'/functions/not_in.R'))
source(paste0(WD,'/functions/rat_mouse_ortho.R'))
source(paste0(WD,'/functions/mouse2rat_ortho.R'))
source(paste0(WD,'/functions/lmp.R'))
source(paste0(WD,'/functions/cor_PC_1_6.R'))
source(paste0(WD,'/functions/elbow_finder.R'))
source(paste0(WD,'/functions/cor_outlier2.R'))
source(paste0(WD,'/functions/DissimilarityMatrixNominal.R'))
source(paste0(WD,'/functions/lm_eqn.R'))
source(paste0(WD,'/functions/reorder_cormat.R'))
source(paste0(WD,'/functions/save_pheatmap_pdf.R'))
source(paste0(WD,'/functions/modeav.R'))
source(paste0(WD,'/functions/count_na.R'))
source(paste0(WD,'/functions/se_mean.R'))
source(paste0(WD,'/functions/Mode.R'))
source(paste0(WD,'/functions/NumericSummaryStats.R'))
source(paste0(WD,'/functions/AutoScaleMatrix.R'))
source(paste0(WD,'/functions/ReverseAutoScaleMatrix.R'))
source(paste0(WD,'/functions/CenterMatrix.R'))
source(paste0(WD,'/functions/RangeScaleMatrix.R'))
source(paste0(WD,'/functions/ParetoScaleMatrix.R'))
source(paste0(WD,'/functions/VastScaleMatrix.R'))
source(paste0(WD,'/functions/LevelScaleMatrix.R'))
source(paste0(WD,'/functions/Log10Matrix.R'))
source(paste0(WD,'/functions/PowerMatrix.R'))

```

##### CSS Styling
```{r Styling}
writeLines("td, th { padding : 3px } th { background-color:white; color:black; border:1px solid black; text-align:center } td {color:black; border:1px solid black; word-wrap:break-word; white-space:nowrap; overflow: hidden; text-overflow: ellipsis; max-width:300px; text-align:left}", con= "../css/style.css")
```

## Comparison of Samples and Metabolites Between Replicate Pairs
  + Split data by replicates
  + Determine the number of missing values per metabolite
  + Determine the number of NA values per metabolite
  + Plot boxplots and matched density plot before normalization
  + Normalize
  + Plot boxplots and matched density plot after normalization

### Orient Data
```{r Orient Data, echo = FALSE}
# Assign Variables
################################################################################
# tissue_study_institute_metab_families <- countdata_df %>%
#   ungroup() %>%
#   unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
#   unite(TISSUE,STUDY_INSTITUTE_METAB_FAMILY, col = TISSUE_STUDY_INSTITUTE_METAB_FAMILY) %>%
#   select(TISSUE_STUDY_INSTITUTE_METAB_FAMILY) %>% unlist() %>% as.character() %>% unique()

# DEV
# tissue_study_institute_metab_family <- "liver_Mayo Clinic_ac"
#for(tissue_study_institute_metab_family in tissue_study_institute_metab_families[1]){
  # Variables
# tissue <- tissue_study_institute_metab_family %>% 
#     str_split(pattern = '_') %>% unlist() %>% head(n=1)
# study_institute_metab_family <- tissue_study_institute_metab_family %>%
#     str_remove(paste0(tissue,'_'))
# named <- 'named'
  
  # Collect the samples (remove QCs) & join sample order
# sample_join <- countdata_df %>%
#         ungroup() %>%
#         unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
#         filter(TISSUE == tissue) %>%
#         filter(NAMED == named) %>%
#         filter(STUDY_INSTITUTE_METAB_FAMILY == study_institute_metab_family) %>%
#         unnest(SAMPLE_DATA) %>%
#         filter(sample_type == 'Sample') %>%
#         select(sample_id, sample_order)

# If the runs contain replicate samples, then proceed with the analysis
# Print the number of replicates
#print(paste0('Number of replicates in ',tissue,' ',study_institute_metab_family,': ', length(reps)))
#print(paste0('Replicates in ',tissue,' ',study_institute_metab_family,': ', paste(reps, collapse = ' ')))

# Ensure the correct replicates
################################################################################
reps <- countdata_df %>%
    ungroup() %>%
    unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
    filter(TISSUE == tissue) %>%
    filter(NAMED == named) %>%
    filter(STUDY_INSTITUTE_METAB_FAMILY == study_institute_metab_family) %>%
    unnest(COUNT_DATA) %>%
    filter(viallabel %in% as.character(unlist(sample_join$sample_id))) %>%
    select(viallabel) %>% unlist() %>% as.character() %>% unique() %>%
    str_sub(-3,-1) %>% unique()

# Collect the metabolites unique to run
################################################################################
metabolites <- countdata_df %>%
        ungroup() %>%
        unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
        filter(TISSUE == tissue) %>%
        filter(NAMED == named) %>%
        filter(STUDY_INSTITUTE_METAB_FAMILY == study_institute_metab_family) %>%
        unnest(METABOLITE_DATA) %>%
        select(refmet_name) %>% unlist() %>% as.character() %>% unique()

# Subset Data
################################################################################
# Collect abundances in long format and annotate replicate labelids
plot_df <- countdata_df %>%
        ungroup() %>%
        unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
        filter(TISSUE == tissue) %>%
        filter(NAMED == named) %>%
        filter(STUDY_INSTITUTE_METAB_FAMILY == study_institute_metab_family) %>%
        unnest(COUNT_DATA) %>%
        filter(viallabel %in% as.character(unlist(sample_join$sample_id))) %>%
        filter(METABOLITE_NAME %in% metabolites) %>%
        left_join(y = sample_join, by = c("viallabel" = "sample_id")) %>%
        unite(labelid, viallabel, col = "labelid_viallabel", remove = F) %>%
        mutate(REPLICATE = case_when(grepl(paste0(reps[1],"$"),labelid_viallabel) ~ reps[1],
                                     grepl(paste0(reps[2],"$"),labelid_viallabel) ~ reps[2],
                                     grepl(paste0(reps[3],"$"),labelid_viallabel) ~ reps[3]))

# Collect Shared Samples
shared_sams <- plot_df %>%
  select(labelid) %>% unique() %>% unlist()
```

### Boxplots (Original Abundances)
```{r Boxplots (Original Abundances)}
# Plot Boxplots faceted by shared metabolites
################################################################################
p <- plot_df %>%
  ggplot(aes(y = METABOLITE_NAME, x = VALUE, color = REPLICATE)) +
  geom_boxplot(alpha = 0.8) +
  labs(title=paste0(tissue,' ',study_institute_metab_family,": Original Metabolite Abundances"),
             x = "Abundance", y = "") 
plot(p)
```

### Zero/Missing Values in Metabolites (Original Abundances)
```{r Zero/Missing Values in Metabolites (Original Abundances)}
# Identify Zero/Missing Values in Metabolites
################################################################################
na_df <- plot_df %>%
  ungroup() %>% 
  group_by(METABOLITE_NAME, REPLICATE) %>%
  mutate(ZERO_LOG = ifelse(VALUE == 0, 1, 0)) %>%
  mutate(ZERO_N = sum(ZERO_LOG)) %>%
  mutate(ZERO_FREQ = round(ZERO_N/length(shared_sams), digits = 2)) %>%
  mutate(NA_LOG = ifelse(is.na(VALUE), 1, 0)) %>%
  mutate(NA_N = sum(NA_LOG)) %>%
  mutate(NA_FREQ = round(NA_N/length(shared_sams), digits = 2)) %>%
  select(REPLICATE, METABOLITE_NAME, ZERO_N, ZERO_FREQ, NA_N, NA_FREQ) %>%
  unique() %>%
  arrange(REPLICATE, desc(ZERO_FREQ), desc(NA_FREQ)) %>%
  ungroup()

na_df %>%
  knitr::kable(format = "html") %>%
  scroll_box(width = "100%", height = "400px")

# Remove Metabolites with high NAor Zero Frequencies
################################################################################
met_rm <- na_df %>%
  filter((ZERO_FREQ >= 0.95) | (NA_FREQ >= 0.8)) %>%
  select(METABOLITE_NAME) %>% unlist() %>% unique()
metabolites <- metabolites[metabolites %!in% met_rm]
plot_df <- plot_df %>%
  filter(METABOLITE_NAME %in% metabolites)
plot_df$METABOLITE_NAME <- as.character(plot_df$METABOLITE_NAME)

```

### Distributions (Original Abundances)
```{r Distributions (Original Abundances)}
# Summary Statistics of Density plot distribution
################################################################################
# Iterate through the runs and collect vectors
df_all <- data.frame()
for(rep in c(reps)){
  # Collect numeric vector
  num_vec <- plot_df %>%
    filter(REPLICATE == rep) %>%
    select(VALUE) %>% unlist() %>% unname()
  df <- NumericSummaryStats(num_vec)
  row.names(df) <- rep
  df_all <- rbind(df_all, df)
}
df_all %>%
  knitr::kable(format = "html") %>%
  scroll_box(width = "100%", height = "200px")

# Plot the density plot for all the gene counts
################################################################################
plot_df %>%
  ggplot(aes(x = VALUE, color = REPLICATE)) +
  geom_density() +
  xlim(min(df_all$MIN), mean(df_all$Q3)) +
  labs(title=paste0(tissue,' ',study_institute_metab_family,": Original Metabolite Abundances"),
       x = "Abundance",
       y = "Density")
```

### Metabolite by Metabolite Correlation (Original Abundances)
```{r Metabolite by Metabolite Correlation (Original Abundances)}
################################################################################
####################### Metabolite by Metabolite Correlations ##################
################################################################################
# Subset Matrices
x <- plot_df %>%
  unite(METABOLITE_NAME,REPLICATE, 
        col = METABOLITE_NAME_REPLICATE, remove = F) %>%
  select(METABOLITE_NAME_REPLICATE, labelid, VALUE,REPLICATE) %>%
  split(.$REPLICATE) %>%
  map(select, -REPLICATE) %>%
  map(pivot_wider, names_from = METABOLITE_NAME_REPLICATE, values_from = VALUE) %>%
  map(arrange, labelid) %>%
  map(tibble::column_to_rownames, var = "labelid") %>%
  map(as.matrix)

# Subset matrices
if(all(row.names(x[[1]]) == row.names(x[[2]]))){
  shared_met_mat <-  do.call(cbind,x) 
}

Corr <- 'Spearman'
# Create an NxN Matrix of correlation
if(Corr == 'Pearson'){
        cor1 <- stats::cor(shared_met_mat, method = 'pearson') %>% round(digits = 3)
}else if(Corr == 'Spearman'){
        cor1 <- stats::cor(shared_met_mat, method = 'spearman') %>% round(digits = 3)
}


# Reorder the correlation matrix
cormat <- cor1

# Melt the correlation matrix
melted_cormat <- melt(cormat, na.rm = TRUE)

################################################################################
####################### Only Reciprocal Pairs ##################################
################################################################################

# Remove rows that compare metabolites from the same dataset, them remove redundent measurements
melted_cormat2 <- melted_cormat 
# Widen the datafrmae back to matrix
cormat2 <- melted_cormat2 %>%
  pivot_wider(names_from = Var2, values_from = value) %>%
  as.data.frame()
row.names(cormat2) <- cormat2$Var1
cormat2 <- cormat2 %>%
  select(-Var1) %>%
  as.matrix()
cormat2 <- cormat2[sort(rownames(cormat2)),sort(colnames(cormat2))]
cormat2 <- cormat2[grepl(reps[1], rownames(cormat2)),grepl(reps[2], colnames(cormat2))]

# Orient the colors and breaks
paletteLength <- 1000
myColor <- colorRampPalette(c("blue", "white", "red"))(paletteLength)
# length(breaks) == length(paletteLength) + 1
# use floor and ceiling to deal with even/odd length pallettelengths
myBreaks <- c(seq(-1, 0, length.out=ceiling(paletteLength/2) + 1), 
              seq(1/paletteLength, max(cor1, na.rm = T), length.out=floor(paletteLength/2)))

# Plot the heatmap
pheatmap(cormat2, color=myColor, breaks=myBreaks, 
                  cluster_rows = F, cluster_cols = F,fontsize = 6)

```

### Scatterplots (Original Abundances)
```{r Scatterplots (Original Abundances)}
# Subset the data for sites to compare (scatterplots)
###################################################
plot_join_df <- countdata_df %>%
  ungroup() %>%
  unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
  filter(TISSUE == tissue) %>%
  filter(NAMED == named) %>%
  filter(STUDY_INSTITUTE_METAB_FAMILY == study_institute_metab_family) %>%
  unnest(COUNT_DATA) %>%
  filter(viallabel %in% as.character(unlist(sample_join$sample_id))) %>%
  filter(METABOLITE_NAME %in% metabolites) %>%
  unite(labelid, viallabel, col = "labelid_viallabel", remove = F) %>%
  mutate(REPLICATE = case_when(grepl(paste0(reps[1],"$"),labelid_viallabel) ~ reps[1],
                              grepl(paste0(reps[2],"$"),labelid_viallabel) ~ reps[2],
                              )) %>%
  select(REPLICATE,METABOLITE_NAME,labelid,VALUE) %>%
  mutate(REPLICATE = as.character(REPLICATE)) %>%
  split(.$REPLICATE) %>%
  map(~rename(., !!sym(unique(.$REPLICATE)) := "VALUE")) %>%
  map(~select(., -REPLICATE)) %>%
  purrr::reduce(left_join, by = c("labelid","METABOLITE_NAME"))

# Plot scatter plots
################################################################################
# Plot scatter plots ordered by sample (include R2 values)
lm_df <- plot_join_df %>%
  rename(name = METABOLITE_NAME) %>%
  rename(x = reps[1]) %>%
  rename(y = reps[2])
# Iterate through each of the shared metabolites to collect summary info about their correlations
r2_df <- data.frame()
for(metab in metabolites){
  met_df <- lm_df %>%
    filter(name == metab)
  r2_df <- rbind(r2_df, lm_eqn(met_df))
}
# Display summaries
met_r2_df <- r2_df %>%
  arrange(METABOLITE) %>%
  select(METABOLITE,R2) %>%
  arrange(desc(R2))
met_r2_df %>%
  knitr::kable(format = "html") %>%
  scroll_box(width = "100%", height = "200px")

# Collect the order of metabolites
scat_met_order <- met_r2_df %>% select(METABOLITE) %>% unlist() %>% as.character()

# Plot the scatter plots
for(metab in scat_met_order){
  p <- plot_join_df %>%
    filter(METABOLITE_NAME == metab) %>%
  ggplot(aes(x = !!sym(reps[1]), y = !!sym(reps[2])), color = ) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", size = 1) +
  geom_abline(linetype="dashed") +
  facet_wrap(~ METABOLITE_NAME) +
  expand_limits(x = 0, y = 0) +
  #labs(title=paste0(tissue,' ',study_institute_metab_family,": Normalized Metabolite Abundances")) +
  coord_fixed(ratio=1)
  plot(p)
}
```

### MA plots (Original Abundances)
```{r MA plots (Original Abundances)}
# Subset the data for sites to compare (scatterplots)
###################################################
plot_join_df <- countdata_df %>%
  ungroup() %>%
  unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
  filter(TISSUE == tissue) %>%
  filter(NAMED == named) %>%
  filter(STUDY_INSTITUTE_METAB_FAMILY == study_institute_metab_family) %>%
  unnest(COUNT_DATA) %>%
  filter(viallabel %in% as.character(unlist(sample_join$sample_id))) %>%
  filter(METABOLITE_NAME %in% metabolites) %>%
  unite(labelid, viallabel, col = "labelid_viallabel", remove = F) %>%
  mutate(REPLICATE = case_when(grepl(paste0(reps[1],"$"),labelid_viallabel) ~ reps[1],
                              grepl(paste0(reps[2],"$"),labelid_viallabel) ~ reps[2],
                              )) %>%
  select(REPLICATE,METABOLITE_NAME,labelid,VALUE) %>%
  mutate(REPLICATE = as.character(REPLICATE)) %>%
  split(.$REPLICATE) %>%
  map(~rename(., !!sym(unique(.$REPLICATE)) := "VALUE")) %>%
  map(~select(., -REPLICATE)) %>%
  purrr::reduce(left_join, by = c("labelid","METABOLITE_NAME"))

# Plot MA plots
################################################################################
# Plot MA plots ordered by sample (include R2 values)
lm_df <- plot_join_df %>%
  rename(name = METABOLITE_NAME) %>%
  rename(x = reps[1]) %>%
  rename(y = reps[2])
# Iterate through each of the shared metabolites to collect summary info about their correlations
r2_df <- data.frame()
for(metab in metabolites){
  met_df <- lm_df %>%
    filter(name == metab)
  r2_df <- rbind(r2_df, lm_eqn(met_df))
}
# Display summaries
met_r2_df <- r2_df %>%
  arrange(METABOLITE) %>%
  select(METABOLITE,R2) %>%
  arrange(desc(R2))

# Collect the order of metabolites
scat_met_order <- met_r2_df %>% select(METABOLITE) %>% unlist() %>% as.character()

# Plot the scatter plots
for(metab in scat_met_order){
  p <- plot_join_df %>%
    filter(METABOLITE_NAME == metab) %>%
  ggplot(aes( x = (log(!!sym(reps[1]) + 1) + log(!!sym(reps[2])) + 1)/2, 
              y = log(!!sym(reps[1]) + 1) - log(!!sym(reps[2]) + 1) ), color = ) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "loess", size = 1) +
  facet_wrap(~ METABOLITE_NAME) +
  ylab('Log Ratio') +
    xlab('Average Log Abundance') +
  #labs(title=paste0(tissue,' ',study_institute_metab_family,": Normalized Metabolite Abundances")) +
  coord_fixed(ratio=1)
  plot(p)
}
```

### Sample by Sample Correlations (Original Abundances)
```{r Sample by Sample Correlations (Original Abundances)}
################################################################################
####################### Sample by Sample Correlations ##########################
################################################################################

# Subset Data
################################################################################
# Original NxP Matrix
x <- plot_df %>%
  unite(labelid,REPLICATE, 
        col = labelid_REPLICATE, remove = F) %>%
  select(labelid_REPLICATE, METABOLITE_NAME, VALUE,REPLICATE) %>%
  split(.$REPLICATE) %>%
  map(select, -REPLICATE) %>%
  map(pivot_wider, names_from = METABOLITE_NAME, values_from = VALUE) %>%
  map(tibble::column_to_rownames, var = "labelid_REPLICATE") %>%
  map(as.matrix)
# Subset matrices
shared_sam_mat <-  do.call(rbind,x) %>% 
  t()

# Create an NxN Matrix of correlation
Corr <- 'Spearman'
if(Corr == 'Pearson'){
        cor1 <- stats::cor(shared_sam_mat, method = 'pearson') %>% round(digits = 3)
}else if(Corr == 'Spearman'){
        cor1 <- stats::cor(shared_sam_mat, method = 'spearman') %>% round(digits = 3)
}

# Melt the correlation matrix
melted_cormat <- melt(cor1, na.rm = TRUE)

################################################################################
####################### Unclustered ############################################
################################################################################

# Remove rows that compare metabolites from the same dataset, them remove redundent measurements
melted_cormat2 <- melted_cormat

# Widen the dataframwe back to matrix
cormat2 <- melted_cormat2 %>%
  pivot_wider(names_from = Var2, values_from = value) %>%
  as.data.frame()
row.names(cormat2) <- cormat2$Var1
cormat2 <- cormat2 %>%
  select(-Var1) %>%
  as.matrix()
cormat2 <- cormat2[sort(rownames(cormat2)),sort(colnames(cormat2))]
cormat2 <- cormat2[grepl(reps[1], rownames(cormat2)),grepl(reps[2], colnames(cormat2))]

# Orient the colors and breaks
paletteLength <- 1000
myColor <- colorRampPalette(c("blue", "white", "red"))(paletteLength)
# length(breaks) == length(paletteLength) + 1
# use floor and ceiling to deal with even/odd length pallettelengths
myBreaks <- c(seq(-1, 0, length.out=ceiling(paletteLength/2) + 1), 
              seq(1/paletteLength, max(cor1, na.rm = TRUE), length.out=floor(paletteLength/2)))

# Plot the heatmap
pheatmap(as.matrix(cormat2), color=myColor, breaks=myBreaks, 
                  cluster_rows = F, cluster_cols = F,fontsize = 6)

```

### PCA Analysis (Original Abundances)
```{r PCA Analysis (Original Abundances)}

pca <- prcomp(na.omit(t(shared_sam_mat)), scale. = F)
percentVar <- pca$sdev^2/sum(pca$sdev^2)
PC <- pca$x %>% as.data.frame()
PC$labelid_rep <- as.character(row.names(pca$x))
PC <- PC %>%
  tidyr::separate(col = labelid_rep, into = c('labelid', 'REPLICATE'),
  sep = "_", remove = T)
# Join the phenotype data
PC <- left_join(PC, pheno_df, by = 'labelid')

p0 <- PC %>%
  ggplot(aes(x = PC1, y = PC2, color=REPLICATE)) +
  geom_point(size = 3) +
  geom_line(aes(group = labelid),color="dark grey") +
  ggtitle('Shared Samples and Shared Metabolites') + 
  xlab(paste0('PC1: ',round(percentVar[1]*100,2),'% variance')) +
  ylab(paste0('PC2: ',round(percentVar[2]*100,2),'% variance')) +
  theme(aspect.ratio=1)
p0
p1 <- PC %>%
        ggplot(aes(x = PC1, y = PC2, color=Key.anirandgroup, shape = REPLICATE)) +
        geom_point(size = 3) +
  geom_line(aes(group = labelid),color="dark grey") +
        ggtitle('Shared Samples and Shared Metabolites') + 
        xlab(paste0('PC1: ',round(percentVar[1]*100,2),'% variance')) +
        ylab(paste0('PC2: ',round(percentVar[2]*100,2),'% variance')) +
        scale_color_manual(values=ec_colors) +
        theme(aspect.ratio=1)
p1
PC$Registration.sex <- as.character(PC$Registration.sex)
p2 <- PC %>%
        ggplot(aes(x = PC1, y = PC2, color=Registration.sex, shape = REPLICATE)) +
        geom_point(size = 3) +
  geom_line(aes(group = labelid),color="dark grey") +
        ggtitle('Shared Samples and Shared Metabolites') + 
        xlab(paste0('PC1: ',round(percentVar[1]*100,2),'% variance')) +
        ylab(paste0('PC2: ',round(percentVar[2]*100,2),'% variance')) +
        theme(aspect.ratio=1)
p2
```

### Normalization (AutoScale)
```{r Normalization}
# Normalize
# Note in this step, we use labelid to account for mayo's duplicate samples
################################################################################
norm_df <- plot_df %>%
  unite(labelid, viallabel, col = "labelid_viallabel", remove = F) %>%
  split(.$REPLICATE) %>%
  map(select, labelid_viallabel, METABOLITE_NAME, VALUE) %>%
  map(pivot_wider, names_from = METABOLITE_NAME, values_from = VALUE) %>%
  map(column_to_rownames, var = "labelid_viallabel") %>%
  map(as.matrix) %>%
  map(AutoScaleMatrix) %>%
  map(as.data.frame) %>%
  map(rownames_to_column, var = "labelid_viallabel") %>%
  map(pivot_longer, names_to = 'METABOLITE_NAME', values_to = 'VALUE', cols = all_of(metabolites)) %>%
  map(mutate, REPLICATE = case_when(grepl(paste0(reps[1],"$"),labelid_viallabel) ~ reps[1],
                                     grepl(paste0(reps[2],"$"),labelid_viallabel) ~ reps[2],
                                    grepl(paste0(reps[3],"$"),labelid_viallabel) ~ reps[3])) %>%
  bind_rows()
```

### Boxplots (Normalized Abundances)
```{r Boxplots (Normalized Abundances)}
# Plot Boxplots faceted by shared metabolites
################################################################################
norm_df %>%
  ggplot(aes(y = METABOLITE_NAME, x = VALUE, color = REPLICATE)) +
  geom_boxplot(alpha = 0.8) +
  labs(title=paste0(tissue,' ',study_institute_metab_family,": Normalized Metabolite Abundances"),
             x = "Abundance", y = "") 
```

### Metabolite by Metabolite Correlation (Normalized Abundances)
```{r Metabolite by Metabolite Correlation (Normalized Abundances)}
################################################################################
####################### Metabolite by Metabolite Correlations ##################
################################################################################
# Subset Matrices
x <- plot_df %>%
  unite(METABOLITE_NAME,REPLICATE, 
        col = METABOLITE_NAME_REPLICATE, remove = F) %>%
  select(METABOLITE_NAME_REPLICATE, labelid, VALUE,REPLICATE) %>%
  split(.$REPLICATE) %>%
  map(select, -REPLICATE) %>%
  map(pivot_wider, names_from = METABOLITE_NAME_REPLICATE, values_from = VALUE) %>%
  map(arrange, labelid) %>%
  map(tibble::column_to_rownames, var = "labelid") %>%
  map(as.matrix) %>%
  map(AutoScaleMatrix)

# Subset matrices
if(all(row.names(x[[1]]) == row.names(x[[2]]))){
  shared_met_mat <-  do.call(cbind,x) 
}

Corr <- 'Spearman'
# Create an NxN Matrix of correlation
if(Corr == 'Pearson'){
        cor1 <- stats::cor(shared_met_mat, method = 'pearson') %>% round(digits = 3)
}else if(Corr == 'Spearman'){
        cor1 <- stats::cor(shared_met_mat, method = 'spearman') %>% round(digits = 3)
}

# Reorder the correlation matrix
cormat <- cor1

# Melt the correlation matrix
melted_cormat <- melt(cormat, na.rm = TRUE)

################################################################################
####################### Only Reciprocal Pairs ##################################
################################################################################

# Remove rows that compare metabolites from the same dataset, them remove redundent measurements
melted_cormat2 <- melted_cormat 
# Widen the datafrmae back to matrix
cormat2 <- melted_cormat2 %>%
  pivot_wider(names_from = Var2, values_from = value) %>%
  as.data.frame()
row.names(cormat2) <- cormat2$Var1
cormat2 <- cormat2 %>%
  select(-Var1) %>%
  as.matrix()
cormat2 <- cormat2[sort(rownames(cormat2)),sort(colnames(cormat2))]
cormat2 <- cormat2[grepl(reps[1], rownames(cormat2)),grepl(reps[2], colnames(cormat2))]

# Orient the colors and breaks
paletteLength <- 1000
myColor <- colorRampPalette(c("blue", "white", "red"))(paletteLength)
# length(breaks) == length(paletteLength) + 1
# use floor and ceiling to deal with even/odd length pallettelengths
myBreaks <- c(seq(-1, 0, length.out=ceiling(paletteLength/2) + 1), 
              seq(1/paletteLength, max(cor1, na.rm = T), length.out=floor(paletteLength/2)))

# Plot the heatmap
pheatmap(cormat2, color=myColor, breaks=myBreaks, 
                  cluster_rows = F, cluster_cols = F,fontsize = 6)

```

### Scatterplots (Normalized Abundances)
```{r Scatterplots (Normalized Abundances)}
# Normalize
# Subset the data for sites to compare (scatterplots)
###################################################
norm_join_df <- countdata_df %>%
  ungroup() %>%
  unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
  filter(TISSUE == tissue) %>%
  filter(NAMED == named) %>%
  filter(STUDY_INSTITUTE_METAB_FAMILY == study_institute_metab_family) %>%
  unnest(COUNT_DATA) %>%
  filter(viallabel %in% as.character(unlist(sample_join$sample_id))) %>%
  unite(labelid, viallabel, col = "labelid_viallabel", remove = F) %>%
  mutate(REPLICATE = case_when(grepl(paste0(reps[1],"$"),labelid_viallabel) ~ reps[1],
                                     grepl(paste0(reps[2],"$"),labelid_viallabel) ~ reps[2],
                               grepl(paste0(reps[3],"$"),labelid_viallabel) ~ reps[3])) %>%
  split(.$REPLICATE) %>%
  map(select, labelid_viallabel, METABOLITE_NAME, VALUE) %>%
  map(pivot_wider, names_from = METABOLITE_NAME, values_from = VALUE) %>%
  map(column_to_rownames, var = "labelid_viallabel") %>%
  map(as.matrix) %>%
  map(AutoScaleMatrix) %>%
  map(as.data.frame) %>%
  map(rownames_to_column, var = "labelid_viallabel") %>%
  map(pivot_longer, names_to = 'METABOLITE_NAME', values_to = 'VALUE', cols = all_of(metabolites)) %>%
  map(mutate, REPLICATE = case_when(grepl(paste0(reps[1],"$"),labelid_viallabel) ~ reps[1],
                                     grepl(paste0(reps[2],"$"),labelid_viallabel) ~ reps[2],
                                    grepl(paste0(reps[3],"$"),labelid_viallabel) ~ reps[3])) %>%
  map(~rename(., !!sym(unique(.$REPLICATE)) := "VALUE")) %>%
  map(~select(., -REPLICATE)) %>%
  map(mutate, labelid = gsub(pattern = "_..*", replacement = '', labelid_viallabel)) %>%
  map(select, -labelid_viallabel) %>%
  purrr::reduce(left_join, by = c("labelid","METABOLITE_NAME"))

# Plot scatter plots ordered by sample (include R2 values)
lm_df <- norm_join_df %>%
  rename(name = METABOLITE_NAME) %>%
  rename(x = reps[1]) %>%
  rename(y = reps[2])
# Iterate through each of the shared metabolites to collect summary info about their correlations
r2_df <- data.frame()
for(metab in metabolites){
  met_df <- lm_df %>%
    filter(name == metab)
  r2_df <- rbind(r2_df, lm_eqn(met_df))
}
# Display summaries
met_r2_df <- r2_df %>%
  arrange(METABOLITE) %>%
  select(METABOLITE,R2) %>%
  arrange(desc(R2))
met_r2_df %>%
  knitr::kable(format = "html") %>%
  scroll_box(width = "100%", height = "200px")

# Collect the order of metabolites
scat_met_order <- met_r2_df %>% select(METABOLITE) %>% unlist() %>% as.character()

# Plot scatter plots (Normalized)
################################################################################
# Plot the scatter plots
for(metab in scat_met_order){
  p <- norm_join_df %>%
    filter(METABOLITE_NAME == metab) %>%
  ggplot(aes(x = !!sym(reps[1]), y = !!sym(reps[2])), color = ) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", size = 1) +
  geom_abline(linetype="dashed") +
  facet_wrap(~ METABOLITE_NAME) +
  expand_limits(x = 0, y = 0) +
  #labs(title=paste0(tissue,' ',study_institute_metab_family,": Normalized Metabolite Abundances")) +
  coord_fixed(ratio=1)
  plot(p)
}
# norm_join_df %>%
#   mutate(METABOLITE_NAME = factor(METABOLITE_NAME, levels = scat_met_order)) %>%
#   ggplot(aes(x = !!sym(reps[1]), y = !!sym(reps[2])), color = ) +
#   geom_point(alpha = 0.5) +
#   geom_smooth(method = "lm", size = 1) +
#   geom_abline(linetype="dashed") +
#   facet_wrap(~ METABOLITE_NAME) +
#   expand_limits(x = 0, y = 0) +
#   labs(title=paste0(tissue,' ',study_institute_metab_family,": Normalized Metabolite Abundances")) +
#   coord_fixed(ratio=1)
```

### MA plots (Normalized Abundances)
```{r Scatterplots (Normalized Abundances)}
# Subset the data for sites to compare (scatterplots)
###################################################
norm_join_df <- countdata_df %>%
  ungroup() %>%
  unite(STUDY_INSTITUTE,METAB_FAMILY, col = "STUDY_INSTITUTE_METAB_FAMILY") %>%
  filter(TISSUE == tissue) %>%
  filter(NAMED == named) %>%
  filter(STUDY_INSTITUTE_METAB_FAMILY == study_institute_metab_family) %>%
  unnest(COUNT_DATA) %>%
  filter(viallabel %in% as.character(unlist(sample_join$sample_id))) %>%
  unite(labelid, viallabel, col = "labelid_viallabel", remove = F) %>%
  mutate(REPLICATE = case_when(grepl(paste0(reps[1],"$"),labelid_viallabel) ~ reps[1],
                                     grepl(paste0(reps[2],"$"),labelid_viallabel) ~ reps[2],
                               grepl(paste0(reps[3],"$"),labelid_viallabel) ~ reps[3])) %>%
  split(.$REPLICATE) %>%
  map(select, labelid_viallabel, METABOLITE_NAME, VALUE) %>%
  map(pivot_wider, names_from = METABOLITE_NAME, values_from = VALUE) %>%
  map(column_to_rownames, var = "labelid_viallabel") %>%
  map(as.matrix) %>%
  map(AutoScaleMatrix) %>%
  map(as.data.frame) %>%
  map(rownames_to_column, var = "labelid_viallabel") %>%
  map(pivot_longer, names_to = 'METABOLITE_NAME', values_to = 'VALUE', cols = all_of(metabolites)) %>%
  map(mutate, REPLICATE = case_when(grepl(paste0(reps[1],"$"),labelid_viallabel) ~ reps[1],
                                     grepl(paste0(reps[2],"$"),labelid_viallabel) ~ reps[2],
                                    grepl(paste0(reps[3],"$"),labelid_viallabel) ~ reps[3])) %>%
  map(~rename(., !!sym(unique(.$REPLICATE)) := "VALUE")) %>%
  map(~select(., -REPLICATE)) %>%
  map(mutate, labelid = gsub(pattern = "_..*", replacement = '', labelid_viallabel)) %>%
  map(select, -labelid_viallabel) %>%
  purrr::reduce(left_join, by = c("labelid","METABOLITE_NAME"))

# Plot MA plots
################################################################################
# Plot MA plots ordered by sample (include R2 values)
lm_df <- norm_join_df %>%
  rename(name = METABOLITE_NAME) %>%
  rename(x = reps[1]) %>%
  rename(y = reps[2])
# Iterate through each of the shared metabolites to collect summary info about their correlations
r2_df <- data.frame()
for(metab in metabolites){
  met_df <- lm_df %>%
    filter(name == metab)
  r2_df <- rbind(r2_df, lm_eqn(met_df))
}
# Display summaries
met_r2_df <- r2_df %>%
  arrange(METABOLITE) %>%
  select(METABOLITE,R2) %>%
  arrange(desc(R2))
met_r2_df %>%
  knitr::kable(format = "html") %>%
  scroll_box(width = "100%", height = "200px")

# Collect the order of metabolites
scat_met_order <- met_r2_df %>% select(METABOLITE) %>% unlist() %>% as.character()


# Plot the MA Plots
################################################################################
for(metab in scat_met_order){
  p <- norm_join_df %>%
    filter(METABOLITE_NAME == metab) %>%
  ggplot(aes( x = (log(!!sym(reps[1])) + log(!!sym(reps[2])))/2, 
              y = log(!!sym(reps[1])) - log(!!sym(reps[2])) ), color = ) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "loess", size = 1) +
  facet_wrap(~ METABOLITE_NAME) +
  ylab('Log Ratio') +
    xlab('Average Log Abundance') +
  #labs(title=paste0(tissue,' ',study_institute_metab_family,": Normalized Metabolite Abundances")) +
  coord_fixed(ratio=1)
  plot(p)
}
```


### Distributions (Normalized Abundances)
```{r Distributions (Normalized Abundances)}
# Plot the density plot for all the gene counts
################################################################################
norm_df %>%
  ggplot(aes(x = VALUE, color = REPLICATE)) +
  geom_density() +
  labs(title=paste0(tissue,' ',study_institute_metab_family,": Normalized Metabolite Abundances"),
       x = "Abundance",
       y = "Density")

# Summary Statistics of Density plot distribution
################################################################################
# Iterate through the runs and collect vectors
df_all <- data.frame()
for(rep in reps){
  # Collect numeric vector
  num_vec <- norm_df %>%
    filter(REPLICATE == rep) %>%
    select(VALUE) %>% unlist() %>% unname()
  df <- NumericSummaryStats(num_vec)
  row.names(df) <- rep
  df_all <- rbind(df_all, df)
}
df_all
#}

```

### Sample by Sample Correlations (Normalized Abundances)
```{r Sample by Sample Correlations (Normalized Abundances)}
################################################################################
####################### Sample by Sample Correlations ##########################
################################################################################

# Subset Data
################################################################################
# Original NxP Matrix
x <- plot_df %>%
  unite(labelid,REPLICATE, 
        col = labelid_REPLICATE, remove = F) %>%
  select(labelid_REPLICATE, METABOLITE_NAME, VALUE,REPLICATE) %>%
  split(.$REPLICATE) %>%
  map(select, -REPLICATE) %>%
  map(pivot_wider, names_from = METABOLITE_NAME, values_from = VALUE) %>%
  map(tibble::column_to_rownames, var = "labelid_REPLICATE") %>%
  map(as.matrix) %>%
  map(AutoScaleMatrix)
# Subset matrices
shared_sam_mat <-  do.call(rbind,x) %>% 
  t()

# Create an NxN Matrix of correlation
Corr <- 'Spearman'
if(Corr == 'Pearson'){
        cor1 <- stats::cor(shared_sam_mat, method = 'pearson') %>% round(digits = 3)
}else if(Corr == 'Spearman'){
        cor1 <- stats::cor(shared_sam_mat, method = 'spearman') %>% round(digits = 3)
}

# Melt the correlation matrix
melted_cormat <- melt(cor1, na.rm = TRUE)

################################################################################
####################### Unclustered ############################################
################################################################################

# Remove rows that compare metabolites from the same dataset, them remove redundent measurements
melted_cormat2 <- melted_cormat

# Widen the dataframwe back to matrix
cormat2 <- melted_cormat2 %>%
  pivot_wider(names_from = Var2, values_from = value) %>%
  as.data.frame()
row.names(cormat2) <- cormat2$Var1
cormat2 <- cormat2 %>%
  select(-Var1) %>%
  as.matrix()
cormat2 <- cormat2[sort(rownames(cormat2)),sort(colnames(cormat2))]
cormat2 <- cormat2[grepl(reps[1], rownames(cormat2)),grepl(reps[2], colnames(cormat2))]

# Orient the colors and breaks
paletteLength <- 1000
myColor <- colorRampPalette(c("blue", "white", "red"))(paletteLength)
# length(breaks) == length(paletteLength) + 1
# use floor and ceiling to deal with even/odd length pallettelengths
myBreaks <- c(seq(-1, 0, length.out=ceiling(paletteLength/2) + 1), 
              seq(1/paletteLength, max(cor1, na.rm = TRUE), length.out=floor(paletteLength/2)))

# Plot the heatmap
pheatmap(as.matrix(cormat2), color=myColor, breaks=myBreaks, 
                  cluster_rows = F, cluster_cols = F,fontsize = 6)

```

### PCA Analysis (Normalized Abundances)
```{r PCA Analysis (Normalized Abundances)}

# Plot a PCA with outliers labeled
# shared_sam_mat <- shared_sam_mat %>%
#   t() %>% AutoScaleMatrix() %>%
#   t()
pca <- prcomp(na.omit(t(shared_sam_mat)), scale. = F)
percentVar <- pca$sdev^2/sum(pca$sdev^2)
PC <- pca$x %>% as.data.frame()
PC$labelid_rep <- as.character(row.names(pca$x))
PC <- PC %>%
  tidyr::separate(col = labelid_rep, into = c('labelid', 'REPLICATE'),
  sep = "_", remove = T)
# Join the phenotype data
PC <- left_join(PC, pheno_df, by = 'labelid')

p0 <- PC %>%
  ggplot(aes(x = PC1, y = PC2, color=REPLICATE)) +
  geom_point(size = 3) +
  geom_line(aes(group = labelid),color="dark grey") +
  ggtitle('Shared Samples and Shared Metabolites') + 
  xlab(paste0('PC1: ',round(percentVar[1]*100,2),'% variance')) +
  ylab(paste0('PC2: ',round(percentVar[2]*100,2),'% variance')) +
  theme(aspect.ratio=1)
p0

p1 <- PC %>%
        ggplot(aes(x = PC1, y = PC2, color=Key.anirandgroup, shape = REPLICATE)) +
        geom_point(size = 3) +
  geom_line(aes(group = labelid),color="dark grey") +
        ggtitle('Shared Samples and Shared Metabolites') + 
        xlab(paste0('PC1: ',round(percentVar[1]*100,2),'% variance')) +
        ylab(paste0('PC2: ',round(percentVar[2]*100,2),'% variance')) +
        scale_color_manual(values=ec_colors) +
        theme(aspect.ratio=1)
p1
PC$Registration.sex <- as.character(PC$Registration.sex)
p2 <- PC %>%
        ggplot(aes(x = PC1, y = PC2, color=Registration.sex, shape = REPLICATE)) +
        geom_point(size = 3) +
  geom_line(aes(group = labelid),color="dark grey") +
        ggtitle('Shared Samples and Shared Metabolites') + 
        xlab(paste0('PC1: ',round(percentVar[1]*100,2),'% variance')) +
        ylab(paste0('PC2: ',round(percentVar[2]*100,2),'% variance')) +
        theme(aspect.ratio=1)
p2

```