---
title: | 
 | PASS1A (Rat) Metabolomics: 
 | Site-Specific EDA--Mayo Clinic
author: "Alec Steep"
date: "10/12/2020"
output:
     html_document:
         code_folding: hide
         toc: true
         highlight: zenburn
         css: ../css/style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(cache = FALSE)
```

##### CSS Styling (auto file write)
```{r Styling}
writeLines("td, th { padding : 3px } th { background-color:white; color:black; border:1px solid black; text-align:center } td {color:black; border:1px solid black; word-wrap:break-word; white-space:nowrap; overflow: hidden; text-overflow: ellipsis; max-width:300px; text-align:left}", con = "../css/style.css")

```

## Goals of Analysis
  + Investigate the (what may be) biological replicates from Mayo

#### Mayo-specific Annotations
  + All targeted
  + No normalization
  + No drift correction
  + No imputation
  + Samples were divided into batches of ~20 for analysis

#### Questions for Mayo:
  + What was the role of QC_POOLED and QC_REFERENCE samples?
  + How were QC samples divided across runs?
  + "raw_file" seems to represent a date and an additiona number (date_#)
    + What is the significance of this number? Does it represent a sample order
  + How was "sample_order" determined?
  + How were batches divided across samples and QCs?
  + Why were some tissues replicated?
  + Demonstrate correlation (or lack thereof) for certain replicate runs.

#### Some runs from Mayo have duplicate abundance measurements
  + Metabolite families:
    + ac, amines, cer, tca
  + Within Tissues:
    + liver, gastrocnemius, white-adipose, lung, heart, brown-adipose, kidney

### Setup the Environment
```{r Setup the Environment, message=FALSE, results='hide', warning = FALSE}
################################################################################
##### Resources and Dependencies ###############################################
################################################################################

# To Render the Markdown, run this line in console
#rmarkdown::render('/Volumes/Frishman_4TB/motrpac/20200915_metabolomics-pass1a/scripts/20201012_pass1a-metabolomics-data-cleanup_steep.Rmd', output_file = '/Volumes/Frishman_4TB/motrpac/20200915_metabolomics-pass1a/reports/mayo_clinic/20201012_replicate-analysis-AAll-tissues-Mayo-Clinic_steep.html')

# Set the working directory
#############################################################################
COMP <- "MacBook" 
#COMP <- "GreatLakes"       
if(COMP == "MacBook"){
        # MacBook
        WD <- '/Volumes/Frishman_4TB/motrpac/20200915_metabolomics-pass1a'    
}else if(COMP == "GreatLakes"){
        # MichMed
        WD <- '/home/acsteep/motrpac/20200915_metabolomics-pass1a'
}

#setwd(WD)

# Load the dependencies
#source("https://bioconductor.org/biocLite.R")
#BiocManager::install("org.Rn.eg.db")
#install.packages("kableExtra")

# Load dependencies
pacs...man <- c("tidyverse", "data.table","rlang","RColorBrewer","MASS","sfsmisc",
                "pheatmap","caret","ggforce","RANN","kableExtra","gtools","combinat",
                "knitr","markdown","rmarkdown")
for(pac in pacs...man){
  suppressWarnings(suppressPackageStartupMessages(library(pac, character.only = TRUE)))
}
# lapply(pacs...man, FUN = function(X) {
#         do.call("library", list(X)) })

############################################################
##### Functions ############################################
############################################################

# Name functions
select <- dplyr::select
counts <- DESeq2::counts
map <- purrr::map
desc <- dplyr::desc
arrange <- dplyr::arrange
melt <- reshape2::melt
mutate <- dplyr::mutate

# Global options
options(dplyr.print_max = 100)
options(scipen=10000)

# Source the functions
source(paste0(WD,'/functions/not_in.R'))
source(paste0(WD,'/functions/rat_mouse_ortho.R'))
source(paste0(WD,'/functions/mouse2rat_ortho.R'))
source(paste0(WD,'/functions/lmp.R'))
source(paste0(WD,'/functions/cor_PC_1_6.R'))
source(paste0(WD,'/functions/elbow_finder.R'))
source(paste0(WD,'/functions/cor_outlier2.R'))
source(paste0(WD,'/functions/DissimilarityMatrixNominal.R'))
source(paste0(WD,'/functions/lm_eqn.R'))
source(paste0(WD,'/functions/reorder_cormat.R'))
source(paste0(WD,'/functions/save_pheatmap_pdf.R'))
source(paste0(WD,'/functions/modeav.R'))
source(paste0(WD,'/functions/count_na.R'))
source(paste0(WD,'/functions/se_mean.R'))
source(paste0(WD,'/functions/Mode.R'))
source(paste0(WD,'/functions/NumericSummaryStats.R'))
source(paste0(WD,'/functions/AutoScaleMatrix.R'))
source(paste0(WD,'/functions/ReverseAutoScaleMatrix.R'))
source(paste0(WD,'/functions/CenterMatrix.R'))
source(paste0(WD,'/functions/RangeScaleMatrix.R'))
source(paste0(WD,'/functions/ParetoScaleMatrix.R'))
source(paste0(WD,'/functions/VastScaleMatrix.R'))
source(paste0(WD,'/functions/LevelScaleMatrix.R'))
source(paste0(WD,'/functions/Log10Matrix.R'))
source(paste0(WD,'/functions/PowerMatrix.R'))

```

### Load the Metadata and Count Data
```{r Load Count Data & MetaData}
# Load the Data
################################################################################
# Files
metadata_rds <- paste0(WD, '/data/20201010_pass1a-metabolomics-metadata-table_steep.rds')
# Load Data
metadata_df <- readRDS(file = metadata_rds)

metadata_df %>%
        head (n = 20) %>%
        knitr::kable(format = "html") %>%
        scroll_box(width = "100%", height = "200px")

# Start the clock
ptm <- proc.time()
# Takes 21+ seconds (881.6 Mb) 1073+ seconds for (7.5Gb)
#countdata_rds <- paste0(WD, #'/data/20201010_pass1a-metabolomics-countdata-nested_steep.rds')

# Load a specific tissues count data
# Liver takes 230 seconds (4 min)
#countdata_rds <- paste0(WD, '/data/20201010_pass1a-metabolomics-countdata-nested-',tissue,'_steep.rds')

# Load a specific metabolite family count data
# ac takes 2 seconds
# hilicpos takes 453 seconds (on MB) or 260 seconds (on GL with 40 MB 2 cores)
# All data (original + autoscaled) takes 170 seconds on MB
countdata_rds <- paste0(WD, '/data/20201010_pass1a-metabolomics-countdata-nested_steep.rds')

# Load the data
#countdata_df <- readRDS(file = countdata_rds)

# Stop the clock
#proc.time() - ptm
```
